---
date: "`r format(Sys.time(), '%d %B, %Y')`"
output:
  word_document: default
---

```{r setup, include=FALSE}
library(here)
library(huxtable)
library(tidyverse)
library(fs)
knitr::opts_chunk$set(echo = FALSE, message = FALSE, warning = FALSE)
# Set a root directory for all chunks to be evaluated relative to rather than the document location
knitr::opts_knit$set(root.dir = here())
```

```{r source, include=FALSE}
here("DataBook", "Modules", "Covid") %>% 
  # list all R files in the directory
  fs::dir_ls(regexp = "\\.R$") %>% 
  # scale up to all R files with a map function from purrr
  map(source, encoding = "UTF-8", local = knitr::knit_global())
```

---
title: "`r set_title`"
author: "`r set_author`"
---


# COVID-19

**Vaccination status**

Description: Proportion of the population who has been vaccinated against COVID-19.

Instrument questions:

- Have you been vaccinated against COVID-19?

```{r covac_c_tbls}
# column names to use with huxtable
covac_c_col_names <- c("Age Group (years)", "n", "%", "95% CI")
covac_c_reg_col_names <- c("Region", "n", "%", "95% CI")

# men, women, both sexes
covac_c_m_w_b <- join_tbls(covac_c, m_w_b, 1, covac_c_col_names)
```
```{r, eval=.GlobalEnv$.u_r_reg==TRUE}
# urban, rural
covac_c_u_r <- join_tbls(covac_c, u_r, 1, covac_c_col_names)
```

<br>

```{r}
cbind(covac_c_m_w_b$m, select(covac_c_m_w_b$w, -agerange), select(covac_c_m_w_b$b, -agerange)) %>% 
  final_tbl(.disaggregation = m_w_b, .s_amount = 3, .title = "Prevalence of vaccinations against COVID-19", .colspan_val = 10)
```

<br>

```{r, eval=.GlobalEnv$.u_r_reg==TRUE}
tbl_m_u_r <- rbind(covac_c_u_r$m_u, covac_c_u_r$m_r)
tbl_w_u_r <- rbind(covac_c_u_r$w_u, covac_c_u_r$w_r)
tbl_b_u_r <- rbind(covac_c_u_r$b_u, covac_c_u_r$b_r)

cbind(tbl_m_u_r, select(tbl_w_u_r, -agerange2), select(tbl_b_u_r, -agerange2)) %>% 
  final_tbl(.disaggregation = u_r, .s_amount = 3, .title = "Prevalence of vaccinations against COVID-19 by type of settlement", .colspan_val = 10)
```

<br>

```{r, eval=.GlobalEnv$.u_r_reg==TRUE}
covac_c$b_reg %>% unite_ci(.ci_amount = 1) %>% apply_hux(.col_names = covac_c_reg_col_names) %>% 
  final_tbl(.disaggregation = reg, .s_amount = 1, .s_val = "Both sexes", .title = "Prevalence of vaccinations against COVID-19 by region", .colspan_val = 4) 
```

<br>

**Analysis information**:

- Questions used: CO1
- R script name: COvac 

***


**Vaccine doses**

Description: Proportion of the population who received a various number of vaccine doses.

Instrument questions:

- Have you been vaccinated against COVID-19?
- How many doses of the vaccine have you received so far?

```{r covacdose_tbls, echo=FALSE}

# column names to use with huxtable
covacdose_c_col_names <- 
  c("Age Group (years)", "n", "% 1 dose", "95% CI", "% 2 doses", "95% CI", 
    "% 3 or more doses", "95% CI")

# column names for region to use with huxtable
covacdose_c_reg_col_names <- 
  c("Region", "n", "% 1 dose", "95% CI", "% 2 doses", "95% CI", 
    "% 3 or more doses", "95% CI")

# men, women, both sexes
covacdose_c_m_w_b <- join_tbls(covacdose_c, m_w_b, 3, covacdose_c_col_names)
```
```{r, eval=.GlobalEnv$.u_r_reg==TRUE}
# urban, rural
covacdose_c_u_r <- join_tbls(covacdose_c, u_r, 3, covacdose_c_col_names)
```

<br>

```{r}
covacdose_c_m_w_b$m %>% 
  set_contents(1, everywhere, covacdose_c_col_names) %>% 
  final_tbl(.disaggregation = m_w_b, .s_amount = 1, .s_val = "Men", .title = "Number of vaccine doses received out of those who are vaccinated", .colspan_val = 8)
```

<br>

```{r}
covacdose_c_m_w_b$w %>% 
  set_contents(1, everywhere, covacdose_c_col_names) %>% 
  final_tbl(.disaggregation = m_w_b, .s_amount = 1, .s_val = "Women", .title = "Number of vaccine doses received out of those who are vaccinated", .colspan_val = 8)
```

<br>

```{r}
covacdose_c_m_w_b$b %>% 
  set_contents(1, everywhere, covacdose_c_col_names) %>% 
  final_tbl(.disaggregation = m_w_b, .s_amount = 1, .s_val = "Both sexes", .title = "Number of vaccine doses received out of those who are vaccinated", .colspan_val = 8)
```

<br>

```{r, eval=.GlobalEnv$.u_r_reg==TRUE}
rbind(covacdose_c_u_r$m_u, covacdose_c_u_r$m_r) %>% 
  set_contents(1, everywhere, covacdose_c_col_names) %>% 
  final_tbl(.disaggregation = u_r, .s_amount = 1, .s_val = "Men", .title = "Number of vaccine doses received out of those who are vaccinated by type of settlement", .colspan_val = 8)
```

<br>

```{r, eval=.GlobalEnv$.u_r_reg==TRUE}
rbind(covacdose_c_u_r$w_u, covacdose_c_u_r$w_r) %>% 
  set_contents(1, everywhere, covacdose_c_col_names) %>% 
  final_tbl(.disaggregation = u_r, .s_amount = 1, .s_val = "Women", .title = "Number of vaccine doses received out of those who are vaccinated by type of settlement", .colspan_val = 8)
```

<br>

```{r, eval=.GlobalEnv$.u_r_reg==TRUE}
rbind(covacdose_c_u_r$b_u, covacdose_c_u_r$b_r) %>% 
  set_contents(1, everywhere, covacdose_c_col_names) %>% 
  final_tbl(.disaggregation = u_r, .s_amount = 1, .s_val = "Both sexes", .title = "Number of vaccine doses received out of those who are vaccinated by type of settlement", .colspan_val = 8)
```

<br>

```{r, eval=.GlobalEnv$.u_r_reg==TRUE}
# region
covacdose_c$b_reg %>% unite_ci(.ci_amount = 3) %>% apply_hux(.col_names = covacdose_c_reg_col_names) %>% 
  final_tbl(.disaggregation = reg, .s_amount = 1, .s_val = "Both sexes", .title = "Number of vaccine doses received out of those who are vaccinated by region", .colspan_val = 8)
```

<br>

**Analysis information**:

- Questions used: CO1, CO2
- R script name:  COvacdose

***


**Vaccination year**

Description: Percentage of vaccinated population by year.

Instrument questions:

- Have you been vaccinated against COVID-19?
- When was the last time you have been vaccinated?

```{r covactime_tbls, echo=FALSE}

# column names to use with huxtable
covactime_col_names <- 
  c("Age Group (years)", "n", "% 2020", "95% CI",
    "% 2021", "95% CI", "% 2022", "95% CI", "% 2023", "95% CI")

# column names for region to use with huxtable
covactime_reg_col_names <- 
  c("Region", "n", "% 2020", "95% CI",
    "% 2021", "95% CI", "% 2022", "95% CI", "% 2023", "95% CI")

# men, women, both sexes
covactime_c_m_w_b <- join_tbls(covactime_c, m_w_b, 4, covactime_col_names)
```
```{r, eval=.GlobalEnv$.u_r_reg==TRUE}
# urban, rural
covactime_c_u_r <- join_tbls(covactime_c, u_r, 4, covactime_col_names)
```

<br>

```{r}
covactime_c_m_w_b$m %>% 
  final_tbl(.disaggregation = m_w_b, .s_val = "Men", .s_amount = 1, .title = "Proportion of the population who had various time of the last vaccination", .colspan_val = 10)
```

<br>

```{r}
covactime_c_m_w_b$w %>% 
  final_tbl(.disaggregation = m_w_b, .s_val = "Women", .s_amount = 1, .title = "Proportion of the population who had various time of the last vaccination", .colspan_val = 10)
```

<br>

```{r}
covactime_c_m_w_b$b %>% 
  final_tbl(.disaggregation = m_w_b, .s_val = "Both sexes", .s_amount = 1, .title = "Proportion of the population who had various time of the last vaccination", .colspan_val = 10)
```

<br>

```{r, eval=.GlobalEnv$.u_r_reg==TRUE}
rbind(covactime_c_u_r$m_u, covactime_c_u_r$m_r) %>% 
  final_tbl(.disaggregation = u_r, .s_val = "Men", .s_amount = 1, .title = "Proportion of the population who had various time of the last vaccination by type of settlement", .colspan_val = 10)
```

<br>

```{r, eval=.GlobalEnv$.u_r_reg==TRUE}
rbind(covactime_c_u_r$w_u, covactime_c_u_r$w_r) %>% 
  final_tbl(.disaggregation = u_r, .s_val = "Women", .s_amount = 1, .title = "Proportion of the population who had various time of the last vaccination by type of settlement", .colspan_val = 10)
```

<br>

```{r, eval=.GlobalEnv$.u_r_reg==TRUE}
rbind(covactime_c_u_r$b_u, covactime_c_u_r$b_r) %>% 
  final_tbl(.disaggregation = u_r, .s_val = "Both sexes", .s_amount = 1, .title = "Proportion of the population who had various time of the last vaccination by type of settlement", .colspan_val = 10)
```

<br>

```{r, eval=.GlobalEnv$.u_r_reg==TRUE}
# region
covactime_c$b_reg %>% unite_ci(.ci_amount = 4) %>% apply_hux(.col_names = covactime_reg_col_names) %>% 
  final_tbl(.disaggregation = reg, .s_amount = 1, .s_val = "Both sexes", .title = "Proportion of the population who had various time of the last vaccination by region", .colspan_val = 10)
```
<br>

**Analysis information**:

- Questions used: CO1, CO2, CO2a
- R script name:  COvactime

***



**Reasons for unvaccinating**

Description: Proportion of the population who had reasons to explain why they are unvaccinated at this time.

Instrument questions:

- Have you been vaccinated against COVID-19?
- Which of the following reasons explain why you are unvaccinated at this time:
a. Inconvenient location of the health facility that offers the vaccine
b. Preferred vaccine option is unavailable
c. You have a medical condition that makes the vaccine unsafe for you
d. Health worker has not recommended the COVID-19 vaccine
e. You have concerns about a severe reaction to the vaccine
f. You do not think the vaccine is safe in general
g. You do not think the vaccine will protect you against severe disease from COVID-19 infection 
h. You believe there might be long-term side effects of the vaccine
i. You do not trust the government/medical authorities
j. You have no concerns about getting infected with COVID-19
k. You believe that natural immunity is better than getting vaccinated
l. Other reason

```{r coreason_tbls}
# column names to use with huxtable
coreason_col_names <- c("Age Group (years)", "n", "%", "95% CI")
coreason_reg_col_names <- c("Region", "n", "%", "95% CI")

# men, women, both sexes
# 1 (a) - Inconvenient location of the health facility that offers the vaccine
coreason_a_m_w_b <- join_tbls(coreason_a, m_w_b, 1, coreason_col_names)
# 2 (b) - Preferred vaccine option is unavailable
coreason_b_m_w_b <- join_tbls(coreason_b, m_w_b, 1, coreason_col_names)
# 3 (c) - Medical condition that makes the vaccine unsafe for the participant
coreason_c_m_w_b <- join_tbls(coreason_c, m_w_b, 1, coreason_col_names)
# 4 (d) - Health worker has not recommended the COVID-19 vaccine
coreason_d_m_w_b <- join_tbls(coreason_d, m_w_b, 1, coreason_col_names)
# 5 (e) - Concerns about a severe reaction to the vaccine
coreason_e_m_w_b <- join_tbls(coreason_e, m_w_b, 1, coreason_col_names)
# 6 (f) - Think the vaccine is unsafe in general
coreason_f_m_w_b <- join_tbls(coreason_f, m_w_b, 1, coreason_col_names)
# 7 (g) - Think the vaccine will not protect them against severe disease from COVID-19 infection
coreason_g_m_w_b <- join_tbls(coreason_g, m_w_b, 1, coreason_col_names)
# 8 (h) - Believe there might be long-term side effects of the vaccine
coreason_h_m_w_b <- join_tbls(coreason_h, m_w_b, 1, coreason_col_names)
# 9 (i) - No trust in the government/medical authorities
coreason_i_m_w_b <- join_tbls(coreason_i, m_w_b, 1, coreason_col_names)
# 10 (j) - No concerns about getting infected with COVID-19
coreason_j_m_w_b <- join_tbls(coreason_j, m_w_b, 1, coreason_col_names)
# 11 (k) - Believe that natural immunity is better than getting vaccinated
coreason_k_m_w_b <- join_tbls(coreason_k, m_w_b, 1, coreason_col_names)
# 12 (l) - Other reason
coreason_l_m_w_b <- join_tbls(coreason_l, m_w_b, 1, coreason_col_names)
```
```{r, eval=.GlobalEnv$.u_r_reg==TRUE}
# urban, rural
# 1 - Inconvenient location of the health facility that offers the vaccine
coreason_a_u_r <- join_tbls(coreason_a, u_r, 1, coreason_col_names)
# 2 - Preferred vaccine option is unavailable
coreason_b_u_r <- join_tbls(coreason_b, u_r, 1, coreason_col_names)
# 3 - Medical condition that makes the vaccine unsafe for the participant
coreason_c_u_r <- join_tbls(coreason_c, u_r, 1, coreason_col_names)
# 4 - Health worker has not recommended the COVID-19 vaccine
coreason_d_u_r <- join_tbls(coreason_d, u_r, 1, coreason_col_names)
# 5 - Concerns about a severe reaction to the vaccine
coreason_e_u_r <- join_tbls(coreason_e, u_r, 1, coreason_col_names)
# 6 - Think the vaccine is unsafe in general
coreason_f_u_r <- join_tbls(coreason_f, u_r, 1, coreason_col_names)
# 7 - Think the vaccine will not protect them against severe disease from COVID-19 infection
coreason_g_u_r <- join_tbls(coreason_g, u_r, 1, coreason_col_names)
# 8 - Believe there might be long-term side effects of the vaccine
coreason_h_u_r <- join_tbls(coreason_h, u_r, 1, coreason_col_names)
# 9 - No trust in the government/medical authorities
coreason_i_u_r <- join_tbls(coreason_i, u_r, 1, coreason_col_names)
# 10 - No concerns about getting infected with COVID-19
coreason_j_u_r <- join_tbls(coreason_j, u_r, 1, coreason_col_names)
# 11 - Believe that natural immunity is better than getting vaccinated
coreason_k_u_r <- join_tbls(coreason_k, u_r, 1, coreason_col_names)
# 12 - Other reason
coreason_l_u_r <- join_tbls(coreason_l, u_r, 1, coreason_col_names)

```

<br>

```{r}
# 1
cbind(coreason_a_m_w_b$m, select(coreason_a_m_w_b$w, -agerange), select(coreason_a_m_w_b$b, -agerange)) %>% final_tbl(.disaggregation = m_w_b, .s_amount = 3, .title = "Inconvenient location of the health facility that offers the vaccine", .colspan_val = 10)
```

<br>

```{r}
# 2
cbind(coreason_b_m_w_b$m, select(coreason_b_m_w_b$w, -agerange), select(coreason_b_m_w_b$b, -agerange)) %>% final_tbl(.disaggregation = m_w_b, .s_amount = 3, .title = "Preferred vaccine option is unavailable", .colspan_val = 10)
```

<br>

```{r}
# 3
cbind(coreason_c_m_w_b$m, select(coreason_c_m_w_b$w, -agerange), select(coreason_c_m_w_b$b, -agerange)) %>% final_tbl(.disaggregation = m_w_b, .s_amount = 3, .title = "Medical condition that makes the vaccine unsafe for the participant", .colspan_val = 10)
```

<br>

```{r}
# 4
cbind(coreason_d_m_w_b$m, select(coreason_d_m_w_b$w, -agerange), select(coreason_d_m_w_b$b, -agerange)) %>% final_tbl(.disaggregation = m_w_b, .s_amount = 3, .title = "Health worker has not recommended the COVID-19 vaccine", .colspan_val = 10)
```

<br>

```{r}
# 5
cbind(coreason_e_m_w_b$m, select(coreason_e_m_w_b$w, -agerange), select(coreason_e_m_w_b$b, -agerange)) %>% final_tbl(.disaggregation = m_w_b, .s_amount = 3, .title = "Concerns about a severe reaction to the vaccine", .colspan_val = 10)
```

<br>

```{r}
# 6
cbind(coreason_f_m_w_b$m, select(coreason_f_m_w_b$w, -agerange), select(coreason_f_m_w_b$b, -agerange)) %>% final_tbl(.disaggregation = m_w_b, .s_amount = 3, .title = "Think the vaccine is unsafe in general", .colspan_val = 10)
```

<br>

```{r}
# 7
cbind(coreason_g_m_w_b$m, select(coreason_g_m_w_b$w, -agerange), select(coreason_g_m_w_b$b, -agerange)) %>% final_tbl(.disaggregation = m_w_b, .s_amount = 3, .title = "Think the vaccine will not protect them against severe disease from COVID-19 infection", .colspan_val = 10)
```

<br>

```{r}
# 8
cbind(coreason_h_m_w_b$m, select(coreason_h_m_w_b$w, -agerange), select(coreason_h_m_w_b$b, -agerange)) %>% final_tbl(.disaggregation = m_w_b, .s_amount = 3, .title = "Believe there might be long-term side effects of the vaccine", .colspan_val = 10)
```

<br>

```{r}
# 9
cbind(coreason_i_m_w_b$m, select(coreason_i_m_w_b$w, -agerange), select(coreason_i_m_w_b$b, -agerange)) %>% final_tbl(.disaggregation = m_w_b, .s_amount = 3, .title = "No trust in the government/medical authorities", .colspan_val = 10)
```

<br>

```{r}
# 10
cbind(coreason_j_m_w_b$m, select(coreason_j_m_w_b$w, -agerange), select(coreason_j_m_w_b$b, -agerange)) %>% final_tbl(.disaggregation = m_w_b, .s_amount = 3, .title = "No concerns about getting infected with COVID-19", .colspan_val = 10)
```

<br>

```{r}
# 11
cbind(coreason_k_m_w_b$m, select(coreason_k_m_w_b$w, -agerange), select(coreason_k_m_w_b$b, -agerange)) %>% final_tbl(.disaggregation = m_w_b, .s_amount = 3, .title = "Believe that natural immunity is better than getting vaccinated", .colspan_val = 10)
```

<br>

```{r}
# 12
cbind(coreason_l_m_w_b$m, select(coreason_l_m_w_b$w, -agerange), select(coreason_l_m_w_b$b, -agerange)) %>% final_tbl(.disaggregation = m_w_b, .s_amount = 3, .title = "Other reason", .colspan_val = 10)
```

<br>

```{r, eval=.GlobalEnv$.u_r_reg==TRUE}
# 1
tbl_m_u_r <- rbind(coreason_a_u_r$m_u, coreason_a_u_r$m_r)
tbl_w_u_r <- rbind(coreason_a_u_r$w_u, coreason_a_u_r$w_r)
tbl_b_u_r <- rbind(coreason_a_u_r$b_u, coreason_a_u_r$b_r)

cbind(tbl_m_u_r, select(tbl_w_u_r, -agerange2), select(tbl_b_u_r, -agerange2)) %>% 
  final_tbl(.disaggregation = u_r, .s_amount = 3, .title = "Inconvenient location of the health facility that offers the vaccine by type of settlement", .colspan_val = 10)
```

<br>

```{r, eval=.GlobalEnv$.u_r_reg==TRUE}
# 2
tbl_m_u_r <- rbind(coreason_b_u_r$m_u, coreason_b_u_r$m_r)
tbl_w_u_r <- rbind(coreason_b_u_r$w_u, coreason_b_u_r$w_r)
tbl_b_u_r <- rbind(coreason_b_u_r$b_u, coreason_b_u_r$b_r)

cbind(tbl_m_u_r, select(tbl_w_u_r, -agerange2), select(tbl_b_u_r, -agerange2)) %>% 
  final_tbl(.disaggregation = u_r, .s_amount = 3, .title = "Preferred vaccine option is unavailable by type of settlement", .colspan_val = 10)
```

<br>

```{r, eval=.GlobalEnv$.u_r_reg==TRUE}
# 3
tbl_m_u_r <- rbind(coreason_c_u_r$m_u, coreason_c_u_r$m_r)
tbl_w_u_r <- rbind(coreason_c_u_r$w_u, coreason_c_u_r$w_r)
tbl_b_u_r <- rbind(coreason_c_u_r$b_u, coreason_c_u_r$b_r)

cbind(tbl_m_u_r, select(tbl_w_u_r, -agerange2), select(tbl_b_u_r, -agerange2)) %>% 
  final_tbl(.disaggregation = u_r, .s_amount = 3, .title = "Medical condition that makes the vaccine unsafe for the participant by type of settlement", .colspan_val = 10)
```

<br>

```{r, eval=.GlobalEnv$.u_r_reg==TRUE}
# 4
tbl_m_u_r <- rbind(coreason_d_u_r$m_u, coreason_d_u_r$m_r)
tbl_w_u_r <- rbind(coreason_d_u_r$w_u, coreason_d_u_r$w_r)
tbl_b_u_r <- rbind(coreason_d_u_r$b_u, coreason_d_u_r$b_r)

cbind(tbl_m_u_r, select(tbl_w_u_r, -agerange2), select(tbl_b_u_r, -agerange2)) %>% 
  final_tbl(.disaggregation = u_r, .s_amount = 3, .title = "Health worker has not recommended the COVID-19 vaccine by type of settlement", .colspan_val = 10)
```

<br>

```{r, eval=.GlobalEnv$.u_r_reg==TRUE}
# 5
tbl_m_u_r <- rbind(coreason_e_u_r$m_u, coreason_e_u_r$m_r)
tbl_w_u_r <- rbind(coreason_e_u_r$w_u, coreason_e_u_r$w_r)
tbl_b_u_r <- rbind(coreason_e_u_r$b_u, coreason_e_u_r$b_r)

cbind(tbl_m_u_r, select(tbl_w_u_r, -agerange2), select(tbl_b_u_r, -agerange2)) %>% 
  final_tbl(.disaggregation = u_r, .s_amount = 3, .title = "Concerns about a severe reaction to the vaccine by type of settlement", .colspan_val = 10)
```

<br>

```{r, eval=.GlobalEnv$.u_r_reg==TRUE}
# 6
tbl_m_u_r <- rbind(coreason_f_u_r$m_u, coreason_f_u_r$m_r)
tbl_w_u_r <- rbind(coreason_f_u_r$w_u, coreason_f_u_r$w_r)
tbl_b_u_r <- rbind(coreason_f_u_r$b_u, coreason_f_u_r$b_r)

cbind(tbl_m_u_r, select(tbl_w_u_r, -agerange2), select(tbl_b_u_r, -agerange2)) %>% 
  final_tbl(.disaggregation = u_r, .s_amount = 3, .title = "Think the vaccine is unsafe in general by type of settlement", .colspan_val = 10)
```

<br>

```{r, eval=.GlobalEnv$.u_r_reg==TRUE}
# 7
tbl_m_u_r <- rbind(coreason_g_u_r$m_u, coreason_g_u_r$m_r)
tbl_w_u_r <- rbind(coreason_g_u_r$w_u, coreason_g_u_r$w_r)
tbl_b_u_r <- rbind(coreason_g_u_r$b_u, coreason_g_u_r$b_r)

cbind(tbl_m_u_r, select(tbl_w_u_r, -agerange2), select(tbl_b_u_r, -agerange2)) %>% 
  final_tbl(.disaggregation = u_r, .s_amount = 3, .title = "Think the vaccine will not protect them against severe disease from COVID-19 infection by type of settlement", .colspan_val = 10)
```

<br>

```{r, eval=.GlobalEnv$.u_r_reg==TRUE}
# 8
tbl_m_u_r <- rbind(coreason_h_u_r$m_u, coreason_h_u_r$m_r)
tbl_w_u_r <- rbind(coreason_h_u_r$w_u, coreason_h_u_r$w_r)
tbl_b_u_r <- rbind(coreason_h_u_r$b_u, coreason_h_u_r$b_r)

cbind(tbl_m_u_r, select(tbl_w_u_r, -agerange2), select(tbl_b_u_r, -agerange2)) %>% 
  final_tbl(.disaggregation = u_r, .s_amount = 3, .title = "Believe there might be long-term side effects of the vaccine by type of settlement", .colspan_val = 10)
```

<br>

```{r, eval=.GlobalEnv$.u_r_reg==TRUE}
# 9
tbl_m_u_r <- rbind(coreason_i_u_r$m_u, coreason_i_u_r$m_r)
tbl_w_u_r <- rbind(coreason_i_u_r$w_u, coreason_i_u_r$w_r)
tbl_b_u_r <- rbind(coreason_i_u_r$b_u, coreason_i_u_r$b_r)

cbind(tbl_m_u_r, select(tbl_w_u_r, -agerange2), select(tbl_b_u_r, -agerange2)) %>% 
  final_tbl(.disaggregation = u_r, .s_amount = 3, .title = "No trust in the government/medical authorities by type of settlement", .colspan_val = 10)
```

<br>

```{r, eval=.GlobalEnv$.u_r_reg==TRUE}
# 10
tbl_m_u_r <- rbind(coreason_j_u_r$m_u, coreason_j_u_r$m_r)
tbl_w_u_r <- rbind(coreason_j_u_r$w_u, coreason_j_u_r$w_r)
tbl_b_u_r <- rbind(coreason_j_u_r$b_u, coreason_j_u_r$b_r)

cbind(tbl_m_u_r, select(tbl_w_u_r, -agerange2), select(tbl_b_u_r, -agerange2)) %>% 
  final_tbl(.disaggregation = u_r, .s_amount = 3, .title = "No concerns about getting infected with COVID-19 by type of settlement", .colspan_val = 10)
```

<br>

```{r, eval=.GlobalEnv$.u_r_reg==TRUE}
# 11
tbl_m_u_r <- rbind(coreason_k_u_r$m_u, coreason_k_u_r$m_r)
tbl_w_u_r <- rbind(coreason_k_u_r$w_u, coreason_k_u_r$w_r)
tbl_b_u_r <- rbind(coreason_k_u_r$b_u, coreason_k_u_r$b_r)

cbind(tbl_m_u_r, select(tbl_w_u_r, -agerange2), select(tbl_b_u_r, -agerange2)) %>% 
  final_tbl(.disaggregation = u_r, .s_amount = 3, .title = "Believe that natural immunity is better than getting vaccinated by type of settlement", .colspan_val = 10)
```

<br>

```{r, eval=.GlobalEnv$.u_r_reg==TRUE}
# 12
tbl_m_u_r <- rbind(coreason_l_u_r$m_u, coreason_l_u_r$m_r)
tbl_w_u_r <- rbind(coreason_l_u_r$w_u, coreason_l_u_r$w_r)
tbl_b_u_r <- rbind(coreason_l_u_r$b_u, coreason_l_u_r$b_r)

cbind(tbl_m_u_r, select(tbl_w_u_r, -agerange2), select(tbl_b_u_r, -agerange2)) %>% 
  final_tbl(.disaggregation = u_r, .s_amount = 3, .title = "Other reason by type of settlement", .colspan_val = 10)
```

<br>

```{r, eval=.GlobalEnv$.u_r_reg==TRUE}
# 1
coreason_a$b_reg %>% unite_ci(.ci_amount = 1) %>% apply_hux(.col_names = coreason_reg_col_names) %>% final_tbl(reg, 1, "Both sexes", "Inconvenient location of the health facility that offers the vaccine by region", 4)
```

<br>

```{r, eval=.GlobalEnv$.u_r_reg==TRUE}
# 2
coreason_b$b_reg %>% unite_ci(.ci_amount = 1) %>% apply_hux(.col_names = coreason_reg_col_names) %>% final_tbl(reg, 1, "Both sexes", "Preferred vaccine option is unavailable by region", 4)
```

<br>

```{r, eval=.GlobalEnv$.u_r_reg==TRUE}
# 3
coreason_c$b_reg %>% unite_ci(.ci_amount = 1) %>% apply_hux(.col_names = coreason_reg_col_names) %>% final_tbl(reg, 1, "Both sexes", "Medical condition that makes the vaccine unsafe for the participant by region", 4)
```

<br>

```{r, eval=.GlobalEnv$.u_r_reg==TRUE}
# 4
coreason_d$b_reg %>% unite_ci(.ci_amount = 1) %>% apply_hux(.col_names = coreason_reg_col_names) %>% final_tbl(reg, 1, "Both sexes", "Health worker has not recommended the COVID-19 vaccine by region", 4)
```

<br>

```{r, eval=.GlobalEnv$.u_r_reg==TRUE}
# 5
coreason_e$b_reg %>% unite_ci(.ci_amount = 1) %>% apply_hux(.col_names = coreason_reg_col_names) %>% final_tbl(reg, 1, "Both sexes", "Concerns about a severe reaction to the vaccine by region", 4)
```

<br>

```{r, eval=.GlobalEnv$.u_r_reg==TRUE}
# 6
coreason_f$b_reg %>% unite_ci(.ci_amount = 1) %>% apply_hux(.col_names = coreason_reg_col_names) %>% final_tbl(reg, 1, "Both sexes", "Think the vaccine is unsafe in general by region", 4)
```

<br>

```{r, eval=.GlobalEnv$.u_r_reg==TRUE}
# 7
coreason_g$b_reg %>% unite_ci(.ci_amount = 1) %>% apply_hux(.col_names = coreason_reg_col_names) %>% final_tbl(reg, 1, "Both sexes", "Think the vaccine will not protect them against severe disease from COVID-19 infection by region", 4)
```

<br>

```{r, eval=.GlobalEnv$.u_r_reg==TRUE}
# 8
coreason_h$b_reg %>% unite_ci(.ci_amount = 1) %>% apply_hux(.col_names = coreason_reg_col_names) %>% final_tbl(reg, 1, "Both sexes", "Believe there might be long-term side effects of the vaccine by region", 4)
```

<br>

```{r, eval=.GlobalEnv$.u_r_reg==TRUE}
# 9
coreason_i$b_reg %>% unite_ci(.ci_amount = 1) %>% apply_hux(.col_names = coreason_reg_col_names) %>% final_tbl(reg, 1, "Both sexes", "No trust in the government/medical authorities by region", 4)
```

<br>

```{r, eval=.GlobalEnv$.u_r_reg==TRUE}
# 10
coreason_j$b_reg %>% unite_ci(.ci_amount = 1) %>% apply_hux(.col_names = coreason_reg_col_names) %>% final_tbl(reg, 1, "Both sexes", "No concerns about getting infected with COVID-19 by region", 4)
```

<br>

```{r, eval=.GlobalEnv$.u_r_reg==TRUE}
# 11
coreason_k$b_reg %>% unite_ci(.ci_amount = 1) %>% apply_hux(.col_names = coreason_reg_col_names) %>% final_tbl(reg, 1, "Both sexes", "Believe that natural immunity is better than getting vaccinated by region", 4)
```

<br>

```{r, eval=.GlobalEnv$.u_r_reg==TRUE}
# 12
coreason_l$b_reg %>% unite_ci(.ci_amount = 1) %>% apply_hux(.col_names = coreason_reg_col_names) %>% final_tbl(reg, 1, "Both sexes", "Other reason by region", 4)
```

<br>

**Analysis information**:

-   Questions used: CO3a-l
-   R script name: COreason

***


**Previous infection**

Description: Proportion of the population who reasonably believe that they have had a COVID-19 infection.

Instrument questions:

- Do you reasonably believe that you have had a COVID-19 infection?

```{r coinfect_tbls, echo=FALSE}

# column names to use with huxtable
coinfect_c_col_names <- 
  c("Age Group (years)", "n", "% Yes, had it once", "95% CI", 
    "% Yes, had it multiple times", "95% CI", 
    "% No", "95% CI")

# column names for region to use with huxtable
coinfect_c_reg_col_names <- 
  c("Region", "n", "% Yes, had it once", "95% CI", 
    "% Yes, had it multiple times", "95% CI", 
    "% No", "95% CI")

# men, women, both sexes
coinfect_c_m_w_b <- join_tbls(coinfect_c, m_w_b, 3, coinfect_c_col_names)
```
```{r, eval=.GlobalEnv$.u_r_reg==TRUE}
# urban, rural
coinfect_c_u_r <- join_tbls(coinfect_c, u_r, 3, coinfect_c_col_names)
```

<br>

```{r}
coinfect_c_m_w_b$m %>% 
  set_contents(1, everywhere, coinfect_c_col_names) %>% 
  final_tbl(.disaggregation = m_w_b, .s_amount = 1, .s_val = "Men", .title = "Percentage of those who reasonably believe they have had a COVID-19 infection", .colspan_val = 8)
```

<br>

```{r}
coinfect_c_m_w_b$w %>% 
  set_contents(1, everywhere, coinfect_c_col_names) %>% 
  final_tbl(.disaggregation = m_w_b, .s_amount = 1, .s_val = "Women", .title = "Percentage of those who reasonably believe they have had a COVID-19 infection", .colspan_val = 8)
```

<br>

```{r}
coinfect_c_m_w_b$b %>% 
  set_contents(1, everywhere, coinfect_c_col_names) %>% 
  final_tbl(.disaggregation = m_w_b, .s_amount = 1, .s_val = "Both sexes", .title = "Percentage of those who reasonably believe they have had a COVID-19 infection", .colspan_val = 8)
```

<br>

```{r, eval=.GlobalEnv$.u_r_reg==TRUE}
rbind(coinfect_c_u_r$m_u, coinfect_c_u_r$m_r) %>% 
  set_contents(1, everywhere, coinfect_c_col_names) %>% 
  final_tbl(.disaggregation = u_r, .s_amount = 1, .s_val = "Men", .title = "Percentage of those who reasonably believe they have had a COVID-19 infection by type of settlement", .colspan_val = 8)
```

<br>

```{r, eval=.GlobalEnv$.u_r_reg==TRUE}
rbind(coinfect_c_u_r$w_u, coinfect_c_u_r$w_r) %>% 
  set_contents(1, everywhere, coinfect_c_col_names) %>% 
  final_tbl(.disaggregation = u_r, .s_amount = 1, .s_val = "Women", .title = "Percentage of those who reasonably believe they have had a COVID-19 infection by type of settlement", .colspan_val = 8)
```

<br>

```{r, eval=.GlobalEnv$.u_r_reg==TRUE}
rbind(coinfect_c_u_r$b_u, coinfect_c_u_r$b_r) %>% 
  set_contents(1, everywhere, coinfect_c_col_names) %>% 
  final_tbl(.disaggregation = u_r, .s_amount = 1, .s_val = "Both sexes", .title = "Percentage of those who reasonably believe they have had a COVID-19 infection by type of settlement", .colspan_val = 8)
```

<br>

```{r, eval=.GlobalEnv$.u_r_reg==TRUE}
# region
coinfect_c$b_reg %>% unite_ci(.ci_amount = 3) %>% apply_hux(.col_names = coinfect_c_reg_col_names) %>% 
  final_tbl(.disaggregation = reg, .s_amount = 1, .s_val = "Both sexes", .title = "Percentage of those who reasonably believe they have had a COVID-19 infection by region", .colspan_val = 8)
```

<br>

**Analysis information**:

- Questions used: CO4
- R script name:  COinfect

***

**Infection confirmed**

Description: Proportion of the population who had their infection either confirmed or not by a test out of those who reasonably believe they have had a COVID-19 infection.

Instrument questions:

- Do you reasonably believe that you have had a COVID-19 infection?
- Was the infection confirmed by a test?

```{r coconfirm_tbls, echo=FALSE}

# column names to use with huxtable
coconfirm_col_names <- 
  c("Age Group (years)", "n", "% Yes, tested positive", "95% CI",
    "% No, tested negative", "95% CI", "% No, didn't want to get tested", "95% CI", 
    "% No, test was unavailable", "95% CI")

# column names for region to use with huxtable
coconfirm_reg_col_names <- 
  c("Region", "n", "% Yes, tested positive", "95% CI",
    "% No, tested negative", "95% CI", "% No, didn't want to get tested", "95% CI", 
    "% No, test was unavailable", "95% CI")

# men, women, both sexes
coconfirm_c_m_w_b <- join_tbls(coconfirm_c, m_w_b, 4, coconfirm_col_names)
```
```{r, eval=.GlobalEnv$.u_r_reg==TRUE}
# urban, rural
coconfirm_c_u_r <- join_tbls(coconfirm_c, u_r, 4, coconfirm_col_names)
```

<br>

```{r}
coconfirm_c_m_w_b$m %>% 
  final_tbl(.disaggregation = m_w_b, .s_val = "Men", .s_amount = 1, .title = "Proportion of the population with confirmed COVID-19 infections by a test", .colspan_val = 10)
```

<br>

```{r}
coconfirm_c_m_w_b$w %>% 
  final_tbl(.disaggregation = m_w_b, .s_val = "Women", .s_amount = 1, .title = "Proportion of the population with confirmed COVID-19 infections by a test", .colspan_val = 10)
```

<br>

```{r}
coconfirm_c_m_w_b$b %>% 
  final_tbl(.disaggregation = m_w_b, .s_val = "Both sexes", .s_amount = 1, .title = "Proportion of the population with confirmed COVID-19 infections by a test", .colspan_val = 10)
```

<br>

```{r, eval=.GlobalEnv$.u_r_reg==TRUE}
rbind(coconfirm_c_u_r$m_u, coconfirm_c_u_r$m_r) %>% 
  final_tbl(.disaggregation = u_r, .s_val = "Men", .s_amount = 1, .title = "Proportion of the population with confirmed COVID-19 infections by a test by type of settlement", .colspan_val = 10)
```

<br>

```{r, eval=.GlobalEnv$.u_r_reg==TRUE}
rbind(coconfirm_c_u_r$w_u, coconfirm_c_u_r$w_r) %>% 
  final_tbl(.disaggregation = u_r, .s_val = "Women", .s_amount = 1, .title = "Proportion of the population with confirmed COVID-19 infections by a test by type of settlement", .colspan_val = 10)
```

<br>

```{r, eval=.GlobalEnv$.u_r_reg==TRUE}
rbind(coconfirm_c_u_r$b_u, coconfirm_c_u_r$b_r) %>% 
  final_tbl(.disaggregation = u_r, .s_val = "Both sexes", .s_amount = 1, .title = "Proportion of the population with confirmed COVID-19 infections by a test by type of settlement", .colspan_val = 10)
```

<br>

```{r, eval=.GlobalEnv$.u_r_reg==TRUE}
# region
coconfirm_c$b_reg %>% unite_ci(.ci_amount = 4) %>% apply_hux(.col_names = coconfirm_reg_col_names) %>% 
  final_tbl(.disaggregation = reg, .s_amount = 1, .s_val = "Both sexes", .title = "Proportion of the population with confirmed COVID-19 infections by a test by region", .colspan_val = 10)
```
<br>

**Analysis information**:

- Questions used: CO4, CO4a
- R script name:  COconfirm

***


**Long COVID symptoms**

Description: Proportion of the population who had symptoms lasting longer than 2 months after the acute infection, which may imply that they may have "Long COVID" or "Post-COVID condition".

Instrument questions:

- Do you reasonably believe that you have had a COVID-19 infection?
- Did you have symptoms which lasted longer than 2 months after the acute infection, which may imply that you may have "Long COVID" or "Post-COVID condition"?

```{r cosymptom_c_tbls}
# column names to use with huxtable
cosymptom_c_col_names <- c("Age Group (years)", "n", "%", "95% CI")
cosymptom_c_reg_col_names <- c("Region", "n", "%", "95% CI")

# men, women, both sexes
cosymptom_c_m_w_b <- join_tbls(cosymptom_c, m_w_b, 1, cosymptom_c_col_names)
```
```{r, eval=.GlobalEnv$.u_r_reg==TRUE}
# urban, rural
cosymptom_c_u_r <- join_tbls(cosymptom_c, u_r, 1, cosymptom_c_col_names)
```

<br>

```{r}
cbind(cosymptom_c_m_w_b$m, select(cosymptom_c_m_w_b$w, -agerange), select(cosymptom_c_m_w_b$b, -agerange)) %>% 
  final_tbl(.disaggregation = m_w_b, .s_amount = 3, .title = "Prevalance of long COVID symptoms", .colspan_val = 10)
```

<br>

```{r, eval=.GlobalEnv$.u_r_reg==TRUE}
tbl_m_u_r <- rbind(cosymptom_c_u_r$m_u, cosymptom_c_u_r$m_r)
tbl_w_u_r <- rbind(cosymptom_c_u_r$w_u, cosymptom_c_u_r$w_r)
tbl_b_u_r <- rbind(cosymptom_c_u_r$b_u, cosymptom_c_u_r$b_r)

cbind(tbl_m_u_r, select(tbl_w_u_r, -agerange2), select(tbl_b_u_r, -agerange2)) %>% 
  final_tbl(.disaggregation = u_r, .s_amount = 3, .title = "Prevalance of long COVID symptoms by type of settlement", .colspan_val = 10)
```

<br>

```{r, eval=.GlobalEnv$.u_r_reg==TRUE}
cosymptom_c$b_reg %>% unite_ci(.ci_amount = 1) %>% apply_hux(.col_names = cosymptom_c_reg_col_names) %>% 
  final_tbl(.disaggregation = reg, .s_amount = 1, .s_val = "Both sexes", .title = "Prevalance of long COVID symptoms by region", .colspan_val = 4) 
```

<br>

**Analysis information**:

- Questions used: CO4, CO5
- R script name: COsymptom

***



**Healthcare services use**

Description: Proportion of the population with symptoms of Long COVID who utilized healthcare services.

Instrument questions:

- Did you have symptoms which lasted longer than 2 months after the acute infection, which may imply that you may have "Long COVID" or "Post-COVID condition"?
- Have you utilized any of the following healthcare services for those long-term symptoms:
a. Primary healthcare services
b. Specialized healthcare services (e.g., hospital)
c. Other healthcare services

```{r coservice_tbls}
# column names to use with huxtable
coservice_col_names <- c("Age Group (years)", "n", "% Utilized", "95% CI")
coservice_reg_col_names <- c("Region", "n", "% Utilized", "95% CI")

# men, women, both sexes
# 1 (a) - Utilized primary healthcare services
coservice_a_m_w_b <- join_tbls(coservice_a, m_w_b, 1, coservice_col_names)

# 2 (b) - Utilized specialized healthcare services (e.g., hospital)
coservice_b_m_w_b <- join_tbls(coservice_b, m_w_b, 1, coservice_col_names)

# 3 (c) - Utilized other healthcare services
coservice_c_m_w_b <- join_tbls(coservice_c, m_w_b, 1, coservice_col_names)
```
```{r, eval=.GlobalEnv$.u_r_reg==TRUE}
# urban, rural
# 1 - Utilized primary healthcare services
coservice_a_u_r <- join_tbls(coservice_a, u_r, 1, coservice_col_names)
# 2 - Utilized specialized healthcare services (e.g., hospital)
coservice_b_u_r <- join_tbls(coservice_b, u_r, 1, coservice_col_names)
# 3 - Utilized other healthcare services
coservice_c_u_r <- join_tbls(coservice_c, u_r, 1, coservice_col_names)
```

<br>

```{r}
# 1
cbind(coservice_a_m_w_b$m, select(coservice_a_m_w_b$w, -agerange), select(coservice_a_m_w_b$b, -agerange)) %>% final_tbl(.disaggregation = m_w_b, .s_amount = 3, .title = "Utilized primary healthcare services", .colspan_val = 10)
```

<br>

```{r}
# 2
cbind(coservice_b_m_w_b$m, select(coservice_b_m_w_b$w, -agerange), select(coservice_b_m_w_b$b, -agerange)) %>% final_tbl(.disaggregation = m_w_b, .s_amount = 3, .title = "Utilized specialized healthcare services (e.g., hospital)", .colspan_val = 10)
```

<br>

```{r}
# 3
cbind(coservice_c_m_w_b$m, select(coservice_c_m_w_b$w, -agerange), select(coservice_c_m_w_b$b, -agerange)) %>% final_tbl(.disaggregation = m_w_b, .s_amount = 3, .title = "Utilized other healthcare services", .colspan_val = 10)
```

<br>


```{r, eval=.GlobalEnv$.u_r_reg==TRUE}
# 1
tbl_m_u_r <- rbind(coservice_a_u_r$m_u, coservice_a_u_r$m_r)
tbl_w_u_r <- rbind(coservice_a_u_r$w_u, coservice_a_u_r$w_r)
tbl_b_u_r <- rbind(coservice_a_u_r$b_u, coservice_a_u_r$b_r)

cbind(tbl_m_u_r, select(tbl_w_u_r, -agerange2), select(tbl_b_u_r, -agerange2)) %>% 
  final_tbl(.disaggregation = u_r, .s_amount = 3, .title = "Utilized primary healthcare services by type of settlement", .colspan_val = 10)
```

<br>

```{r, eval=.GlobalEnv$.u_r_reg==TRUE}
# 2
tbl_m_u_r <- rbind(coservice_b_u_r$m_u, coservice_b_u_r$m_r)
tbl_w_u_r <- rbind(coservice_b_u_r$w_u, coservice_b_u_r$w_r)
tbl_b_u_r <- rbind(coservice_b_u_r$b_u, coservice_b_u_r$b_r)

cbind(tbl_m_u_r, select(tbl_w_u_r, -agerange2), select(tbl_b_u_r, -agerange2)) %>% 
  final_tbl(.disaggregation = u_r, .s_amount = 3, .title = "Utilized specialized healthcare services (e.g., hospital) by type of settlement", .colspan_val = 10)
```

<br>

```{r, eval=.GlobalEnv$.u_r_reg==TRUE}
# 3
tbl_m_u_r <- rbind(coservice_c_u_r$m_u, coservice_c_u_r$m_r)
tbl_w_u_r <- rbind(coservice_c_u_r$w_u, coservice_c_u_r$w_r)
tbl_b_u_r <- rbind(coservice_c_u_r$b_u, coservice_c_u_r$b_r)

cbind(tbl_m_u_r, select(tbl_w_u_r, -agerange2), select(tbl_b_u_r, -agerange2)) %>% 
  final_tbl(.disaggregation = u_r, .s_amount = 3, .title = "Utilized other healthcare services by type of settlement", .colspan_val = 10)
```

<br>

```{r, eval=.GlobalEnv$.u_r_reg==TRUE}
# 1
coservice_a$b_reg %>% unite_ci(.ci_amount = 1) %>% apply_hux(.col_names = coservice_reg_col_names) %>% final_tbl(reg, 1, "Both sexes", "Utilized primary healthcare services by region", 4)
```

<br>

```{r, eval=.GlobalEnv$.u_r_reg==TRUE}
# 2
coservice_b$b_reg %>% unite_ci(.ci_amount = 1) %>% apply_hux(.col_names = coservice_reg_col_names) %>% final_tbl(reg, 1, "Both sexes", "Utilized specialized healthcare services (e.g., hospital) by region", 4)
```

<br>

```{r, eval=.GlobalEnv$.u_r_reg==TRUE}
# 3
coservice_c$b_reg %>% unite_ci(.ci_amount = 1) %>% apply_hux(.col_names = coservice_reg_col_names) %>% final_tbl(reg, 1, "Both sexes", "Utilized other healthcare services by region", 4)
```

<br>

**Analysis information**:

- Questions used: CO5, CO6a-c
- R script name: COservice

***



**Effects of long COVID**

Description: Proportion of the population with long-term symptoms that reduce their ability to carry out day-to-day activities compared with the time before they had COVID-19.

Instrument questions:

- Did you have symptoms which lasted longer than 2 months after the acute infection, which may imply that you may have "Long COVID" or "Post-COVID condition"?
- Do those long-term symptoms reduce your ability to carry out day-to-day activities compared with the time before you had COVID-19?

```{r coability_tbls, echo=FALSE}

# column names to use with huxtable
coability_c_col_names <- 
  c("Age Group (years)", "n", "% Yes, a lot", "95% CI", "% Yes, a little", "95% CI", 
    "% Not at all", "95% CI")

# column names for region to use with huxtable
coability_c_reg_col_names <- 
  c("Region", "n", "% Yes, a lot", "95% CI", "% Yes, a little", "95% CI", 
    "% Not at all", "95% CI")

# men, women, both sexes
coability_c_m_w_b <- join_tbls(coability_c, m_w_b, 3, coability_c_col_names)
```
```{r, eval=.GlobalEnv$.u_r_reg==TRUE}
# urban, rural
coability_c_u_r <- join_tbls(coability_c, u_r, 3, coability_c_col_names)
```

<br>

```{r}
coability_c_m_w_b$m %>% 
  set_contents(1, everywhere, coability_c_col_names) %>% 
  final_tbl(.disaggregation = m_w_b, .s_amount = 1, .s_val = "Men", .title = "Effects of long COVID on ability to carry out day-to-day activities", .colspan_val = 8)
```

<br>

```{r}
coability_c_m_w_b$w %>% 
  set_contents(1, everywhere, coability_c_col_names) %>% 
  final_tbl(.disaggregation = m_w_b, .s_amount = 1, .s_val = "Women", .title = "Effects of long COVID on ability to carry out day-to-day activities", .colspan_val = 8)
```

<br>

```{r}
coability_c_m_w_b$b %>% 
  set_contents(1, everywhere, coability_c_col_names) %>% 
  final_tbl(.disaggregation = m_w_b, .s_amount = 1, .s_val = "Both sexes", .title = "Effects of long COVID on ability to carry out day-to-day activities", .colspan_val = 8)
```

<br>

```{r, eval=.GlobalEnv$.u_r_reg==TRUE}
rbind(coability_c_u_r$m_u, coability_c_u_r$m_r) %>% 
  set_contents(1, everywhere, coability_c_col_names) %>% 
  final_tbl(.disaggregation = u_r, .s_amount = 1, .s_val = "Men", .title = "Effects of long COVID on ability to carry out day-to-day activities by type of settlement", .colspan_val = 8)
```

<br>

```{r, eval=.GlobalEnv$.u_r_reg==TRUE}
rbind(coability_c_u_r$w_u, coability_c_u_r$w_r) %>% 
  set_contents(1, everywhere, coability_c_col_names) %>% 
  final_tbl(.disaggregation = u_r, .s_amount = 1, .s_val = "Women", .title = "Effects of long COVID on ability to carry out day-to-day activities by type of settlement", .colspan_val = 8)
```

<br>

```{r, eval=.GlobalEnv$.u_r_reg==TRUE}
rbind(coability_c_u_r$b_u, coability_c_u_r$b_r) %>% 
  set_contents(1, everywhere, coability_c_col_names) %>% 
  final_tbl(.disaggregation = u_r, .s_amount = 1, .s_val = "Both sexes", .title = "Effects of long COVID on ability to carry out day-to-day activities by type of settlement", .colspan_val = 8)
```

<br>

```{r, eval=.GlobalEnv$.u_r_reg==TRUE}
# region
coability_c$b_reg %>% unite_ci(.ci_amount = 3) %>% apply_hux(.col_names = coability_c_reg_col_names) %>% 
  final_tbl(.disaggregation = reg, .s_amount = 1, .s_val = "Both sexes", .title = "Effects of long COVID on ability to carry out day-to-day activities by region", .colspan_val = 8)
```

<br>

**Analysis information**:

- Questions used: CO5, CO7
- R script name:  COability

***



**Time off due to long COVID**

Description: Proportion of the population who required time off work or studying due to long COVID symptoms.

Instrument questions:

- Did you have symptoms which lasted longer than 2 months after the acute infection, which may imply that you may have "Long COVID" or "Post-COVID condition"?
- Did you require time off work or studying due to long COVID symptoms?

```{r cotimeoff_tbls, echo=FALSE}

# column names to use with huxtable
cotimeoff_c_col_names <- 
  c("Age Group (years)", "n", "% Yes", "95% CI", "% No", "95% CI", 
    "% Don’t work or study", "95% CI")

# column names for region to use with huxtable
cotimeoff_c_reg_col_names <- 
  c("Region", "n", "% Yes", "95% CI", "% No", "95% CI", 
    "% Don’t work or study", "95% CI")

# men, women, both sexes
cotimeoff_c_m_w_b <- join_tbls(cotimeoff_c, m_w_b, 3, cotimeoff_c_col_names)
```
```{r, eval=.GlobalEnv$.u_r_reg==TRUE}
# urban, rural
cotimeoff_c_u_r <- join_tbls(cotimeoff_c, u_r, 3, cotimeoff_c_col_names)
```

<br>

```{r}
cotimeoff_c_m_w_b$m %>% 
  set_contents(1, everywhere, cotimeoff_c_col_names) %>% 
  final_tbl(.disaggregation = m_w_b, .s_amount = 1, .s_val = "Men", .title = "Time off work or studying due to long COVID symptoms", .colspan_val = 8)
```

<br>

```{r}
cotimeoff_c_m_w_b$w %>% 
  set_contents(1, everywhere, cotimeoff_c_col_names) %>% 
  final_tbl(.disaggregation = m_w_b, .s_amount = 1, .s_val = "Women", .title = "Time off work or studying due to long COVID symptoms", .colspan_val = 8)
```

<br>

```{r}
cotimeoff_c_m_w_b$b %>% 
  set_contents(1, everywhere, cotimeoff_c_col_names) %>% 
  final_tbl(.disaggregation = m_w_b, .s_amount = 1, .s_val = "Both sexes", .title = "Time off work or studying due to long COVID symptoms", .colspan_val = 8)
```

<br>

```{r, eval=.GlobalEnv$.u_r_reg==TRUE}
rbind(cotimeoff_c_u_r$m_u, cotimeoff_c_u_r$m_r) %>% 
  set_contents(1, everywhere, cotimeoff_c_col_names) %>% 
  final_tbl(.disaggregation = u_r, .s_amount = 1, .s_val = "Men", .title = "Time off work or studying due to long COVID symptoms by type of settlement", .colspan_val = 8)
```

<br>

```{r, eval=.GlobalEnv$.u_r_reg==TRUE}
rbind(cotimeoff_c_u_r$w_u, cotimeoff_c_u_r$w_r) %>% 
  set_contents(1, everywhere, cotimeoff_c_col_names) %>% 
  final_tbl(.disaggregation = u_r, .s_amount = 1, .s_val = "Women", .title = "Time off work or studying due to long COVID symptoms by type of settlement", .colspan_val = 8)
```

<br>

```{r, eval=.GlobalEnv$.u_r_reg==TRUE}
rbind(cotimeoff_c_u_r$b_u, cotimeoff_c_u_r$b_r) %>% 
  set_contents(1, everywhere, cotimeoff_c_col_names) %>% 
  final_tbl(.disaggregation = u_r, .s_amount = 1, .s_val = "Both sexes", .title = "Time off work or studying due to long COVID symptoms by type of settlement", .colspan_val = 8)
```

<br>

```{r, eval=.GlobalEnv$.u_r_reg==TRUE}
# region
cotimeoff_c$b_reg %>% unite_ci(.ci_amount = 3) %>% apply_hux(.col_names = cotimeoff_c_reg_col_names) %>% 
  final_tbl(.disaggregation = reg, .s_amount = 1, .s_val = "Both sexes", .title = "Time off work or studying due to long COVID symptoms by region", .colspan_val = 8)
```

<br>

**Analysis information**:

- Questions used: CO5, CO8
- R script name:  COtimeoff

***



**Time off duration**

Description: Mean number of days required for time off work or studying.

Instrument questions:

- Did you require time off work or studying due to long COVID symptoms?
- For how long?

```{r cotimeoff_co8adays_tbls}

# column names to use with huxtable
cotimeoff_co8adays_col_names <- c("Age Group (years)", "n", "Mean number", "95% CI")

# column names for region to use with huxtable
cotimeoff_co8adays_reg_col_names <- c("Region", "n", "Mean number", "95% CI")

# men, women, both sexes
cotimeoff_co8adays_m_w_b <- join_tbls(cotimeoff_co8adays, m_w_b, 1, cotimeoff_co8adays_col_names)
```
```{r, eval=.GlobalEnv$.u_r_reg==TRUE}
# urban, rural
cotimeoff_co8adays_u_r <- join_tbls(cotimeoff_co8adays, u_r, 1, cotimeoff_co8adays_col_names)
```

<br>

```{r}
cbind(cotimeoff_co8adays_m_w_b$m, select(cotimeoff_co8adays_m_w_b$w, -agerange), 
      select(cotimeoff_co8adays_m_w_b$b, -agerange)) %>% 
  final_tbl(.disaggregation = m_w_b, 3, .title = "Mean number of days required for time off work or studying", .colspan_val = 10)
```

<br>

```{r, eval=.GlobalEnv$.u_r_reg==TRUE}
tbl_m_u_r <- rbind(cotimeoff_co8adays_u_r$m_u, cotimeoff_co8adays_u_r$m_r)
tbl_w_u_r <- rbind(cotimeoff_co8adays_u_r$w_u, cotimeoff_co8adays_u_r$w_r)
tbl_b_u_r <- rbind(cotimeoff_co8adays_u_r$b_u, cotimeoff_co8adays_u_r$b_r)

cbind(tbl_m_u_r, select(tbl_w_u_r, -agerange2), select(tbl_b_u_r, -agerange2)) %>% 
  final_tbl(.disaggregation = u_r, .s_amount = 3, .title = "Mean number of days required for time off work or studying by type of settlement", .colspan_val = 10)
```

<br>

```{r, eval=.GlobalEnv$.u_r_reg==TRUE}
# region
cotimeoff_co8adays$b_reg %>% unite_ci(.ci_amount = 1) %>% apply_hux(.col_names = cotimeoff_co8adays_reg_col_names) %>% 
  final_tbl(.disaggregation = reg, .s_amount = 1, .s_val = "Both sexes", .title = "Mean number of days required for time off work or studying by region", .colspan_val = 4)
```

<br>

**Analysis information**:

- Questions used: CO8, CO8a, CO8a_type
- R script name:  COtimeoff

***



**Long COVID symptoms resolution**

Description: Proportion of the population who feel their long COVID symptoms have been resolved.

Instrument questions:

- Did you have symptoms which lasted longer than 2 months after the acute infection, which may imply that you may have "Long COVID" or "Post-COVID condition"?
- Do you feel your long-term symptoms have now resolved?

```{r coresolved_c_tbls}
# column names to use with huxtable
coresolved_c_col_names <- c("Age Group (years)", "n", "%", "95% CI")
coresolved_c_reg_col_names <- c("Region", "n", "%", "95% CI")

# men, women, both sexes
coresolved_c_m_w_b <- join_tbls(coresolved_c, m_w_b, 1, coresolved_c_col_names)
```
```{r, eval=.GlobalEnv$.u_r_reg==TRUE}
# urban, rural
coresolved_c_u_r <- join_tbls(coresolved_c, u_r, 1, coresolved_c_col_names)
```

<br>

```{r}
cbind(coresolved_c_m_w_b$m, select(coresolved_c_m_w_b$w, -agerange), select(coresolved_c_m_w_b$b, -agerange)) %>% 
  final_tbl(.disaggregation = m_w_b, .s_amount = 3, .title = "Proportion of the population who feel their long COVID symptoms have been resolved", .colspan_val = 10)
```

<br>

```{r, eval=.GlobalEnv$.u_r_reg==TRUE}
tbl_m_u_r <- rbind(coresolved_c_u_r$m_u, coresolved_c_u_r$m_r)
tbl_w_u_r <- rbind(coresolved_c_u_r$w_u, coresolved_c_u_r$w_r)
tbl_b_u_r <- rbind(coresolved_c_u_r$b_u, coresolved_c_u_r$b_r)

cbind(tbl_m_u_r, select(tbl_w_u_r, -agerange2), select(tbl_b_u_r, -agerange2)) %>% 
  final_tbl(.disaggregation = u_r, .s_amount = 3, .title = "Proportion of the population who feel their long COVID symptoms have been resolved by type of settlement", .colspan_val = 10)
```

<br>

```{r, eval=.GlobalEnv$.u_r_reg==TRUE}
coresolved_c$b_reg %>% unite_ci(.ci_amount = 1) %>% apply_hux(.col_names = coresolved_c_reg_col_names) %>% 
  final_tbl(.disaggregation = reg, .s_amount = 1, .s_val = "Both sexes", .title = "Proportion of the population who feel their long COVID symptoms have been resolved by region", .colspan_val = 4) 
```

<br>

**Analysis information**:

- Questions used: CO5, CO8a_type, CO9
- R script name: COresolved

***


<br>
<br>
