---
date: "`r format(Sys.time(), '%d %B, %Y')`"
output:
  word_document: default
---

```{r setup, include=FALSE}
library(here)
library(huxtable)
library(tidyverse)
library(fs)
knitr::opts_chunk$set(echo = FALSE, message = FALSE, warning = FALSE)
# Set a root directory for all chunks to be evaluated relative to rather than the document location
knitr::opts_knit$set(root.dir = here())
```

```{r source, include=FALSE}
diet_data_dir <- here("DataBook", "Modules", "Diet")

# read in each R file, because in KGZ not all scripts in the Diet module are used
source(here(diet_data_dir, "DX1.R"))
source(here(diet_data_dir, "Ddays.R"))
source(here(diet_data_dir, "Dservings.R"))
source(here(diet_data_dir, "Dfiveormore.R"))
source(here(diet_data_dir, "Dcontrol.R"))
source(here(diet_data_dir, "Dcooking.R"))
source(here(diet_data_dir, "Deating.R"))
source(here(diet_data_dir, "Dhealth.R"))
source(here(diet_data_dir, "Dlower.R"))
#source(here(diet_data_dir, "Dmealsout.R")) # no d13
#source(here(diet_data_dir, "Doil.R")) # no d12
source(here(diet_data_dir, "Dsaltquantity.R"))
source(here(diet_data_dir, "Dprocessed.R"))

```

---
title: "`r set_title`"
author: "`r set_author`"
---

# Diet

**Mean number of days of fruit and vegetable consumption**

Description: mean number of days fruit and vegetables consumed.

Instrument questions:

- In a typical week, on how many days do you eat fruit?
- In a typical week, on how many days do you eat vegetables?

```{r ddays_tbls}

# column names to use with huxtable
ddays_col_names <- c("Age Group (years)", "n", "Mean number of days", "95% CI")
ddays_reg_col_names <- c("Region", "n", "Mean number of days", "95% CI")

# 1. Fruit
# men, women, both sexes
ddays_d1_m_w_b <- join_tbls(ddays_d1, m_w_b, 1, ddays_col_names)
# 2. Vegetables
# men, women, both sexes
ddays_d3_m_w_b <- join_tbls(ddays_d3, m_w_b, 1, ddays_col_names)
```
```{r, eval=.GlobalEnv$.u_r_reg==TRUE}
# urban, rural
# 1. Fruit
ddays_d1_u_r <- join_tbls(ddays_d1, u_r, 1, ddays_col_names)
# 2. Vegetable
ddays_d3_u_r <- join_tbls(ddays_d3, u_r, 1, ddays_col_names)
```

<br>

```{r}
# 1. Fruit
cbind(ddays_d1_m_w_b$m, select(ddays_d1_m_w_b$w, -agerange), select(ddays_d1_m_w_b$b, -agerange)) %>% 
  final_tbl(.disaggregation = m_w_b, .s_amount = 3, .title = "Mean number of days fruit consumed in a typical week", .colspan_val = 10)
```

<br>

```{r}
# 2. Vegetables
cbind(ddays_d3_m_w_b$m, select(ddays_d3_m_w_b$w, -agerange), select(ddays_d3_m_w_b$b, -agerange)) %>% 
  final_tbl(.disaggregation = m_w_b, .s_amount = 3, .title = "Mean number of days vegetables consumed in a typical week", .colspan_val = 10)
```

<br>

```{r, eval=.GlobalEnv$.u_r_reg==TRUE}
# 1. Fruit
tbl_m_u_r <- rbind(ddays_d1_u_r$m_u, ddays_d1_u_r$m_r)
tbl_w_u_r <- rbind(ddays_d1_u_r$w_u, ddays_d1_u_r$w_r)
tbl_b_u_r <- rbind(ddays_d1_u_r$b_u, ddays_d1_u_r$b_r)

cbind(tbl_m_u_r, select(tbl_w_u_r, -agerange2), select(tbl_b_u_r, -agerange2)) %>% 
  final_tbl(.disaggregation = u_r, .s_amount = 3, .title = "Mean number of days fruit consumed in a typical week by type of settlement", .colspan_val = 10)
```

<br>

```{r, eval=.GlobalEnv$.u_r_reg==TRUE}
# 2. Vegetables
tbl_m_u_r <- rbind(ddays_d3_u_r$m_u, ddays_d3_u_r$m_r)
tbl_w_u_r <- rbind(ddays_d3_u_r$w_u, ddays_d3_u_r$w_r)
tbl_b_u_r <- rbind(ddays_d3_u_r$b_u, ddays_d3_u_r$b_r)

cbind(tbl_m_u_r, select(tbl_w_u_r, -agerange2), select(tbl_b_u_r, -agerange2)) %>% 
  final_tbl(.disaggregation = u_r, .s_amount = 3, .title = "Mean number of days vegetables consumed in a typical week by type of settlement", .colspan_val = 10)
```

<br>

```{r, eval=.GlobalEnv$.u_r_reg==TRUE}
ddays_d1$b_reg %>% unite_ci(.ci_amount = 1) %>% apply_hux(.col_names = ddays_reg_col_names) %>% 
  final_tbl(.disaggregation = reg, 1, "Both sexes", "Mean number of days fruit consumed in a typical week by region", 4) 
```

<br>

```{r, eval=.GlobalEnv$.u_r_reg==TRUE}
ddays_d3$b_reg %>% unite_ci(.ci_amount = 1) %>% apply_hux(.col_names = ddays_reg_col_names) %>% 
  final_tbl(.disaggregation = reg, 1, "Both sexes", "Mean number of days vegetables consumed in a typical week by region", 4) 
```

<br>

**Analysis information**:

- Questions used: D1, D3
- R script name: Ddays

***

**Mean number of servings of fruit and vegetable consumption**

Description: mean number of fruit, vegetable, and combined fruit and vegetable servings on average per day.

Instrument questions:

- In a typical week, on how many days do you eat fruit?
- How many servings of fruit do you eat on one of those days?
- In a typical week, on how many days do you eat vegetables?
- How many servings of vegetables do you eat on one of those days?

```{r dservings_tbls}

# column names to use with huxtable
dservings_col_names <- c("Age Group (years)", "n", "Mean number of servings", "95% CI")
dservings_reg_col_names <- c("Region", "n", "Mean number of servings", "95% CI")

# 1. Fruit
# men, women, both sexes
fservings_tbls_m_w_b <- join_tbls(fservings_tbls, m_w_b, 1, dservings_col_names)
# 2. Vegetables
# men, women, both sexes
vservings_tbls_m_w_b <- join_tbls(vservings_tbls, m_w_b, 1, dservings_col_names)
# 3. Fruit and/or vegetables
# men, women, both sexes
fvservings_tbls_m_w_b <- join_tbls(fvservings_tbls, m_w_b, 1, dservings_col_names)
```
```{r, eval=.GlobalEnv$.u_r_reg==TRUE}
# urban, rural
# 1. Fruit
fservings_tbls_u_r <- join_tbls(fservings_tbls, u_r, 1, dservings_col_names)
# 2. Vegetable
vservings_tbls_u_r <- join_tbls(vservings_tbls, u_r, 1, dservings_col_names)
# 3. Fruit and/or vegetables
fvservings_tbls_u_r <- join_tbls(fvservings_tbls, u_r, 1, dservings_col_names)
```

<br>

```{r}
# 1. Fruit
cbind(fservings_tbls_m_w_b$m, select(fservings_tbls_m_w_b$w, -agerange), select(fservings_tbls_m_w_b$b, -agerange)) %>% 
  final_tbl(.disaggregation = m_w_b, .s_amount = 3, .title = "Mean number of servings of fruit on average per day", .colspan_val = 10)
```

<br>

```{r}
# 2. Vegetables
cbind(vservings_tbls_m_w_b$m, select(vservings_tbls_m_w_b$w, -agerange), select(vservings_tbls_m_w_b$b, -agerange)) %>% 
  final_tbl(.disaggregation = m_w_b, .s_amount = 3, .title = "Mean number of servings of vegetables on average per day", .colspan_val = 10)
```

<br>

```{r}
# 3. Fruit and/or vegetables
cbind(fvservings_tbls_m_w_b$m, select(fvservings_tbls_m_w_b$w, -agerange), select(fvservings_tbls_m_w_b$b, -agerange)) %>% 
  final_tbl(.disaggregation = m_w_b, .s_amount = 3, .title = "Mean number of servings of fruit and/or vegetables on average per day", .colspan_val = 10)
```

<br>

```{r, eval=.GlobalEnv$.u_r_reg==TRUE}
# 1. Fruit
tbl_m_u_r <- rbind(fservings_tbls_u_r$m_u, fservings_tbls_u_r$m_r)
tbl_w_u_r <- rbind(fservings_tbls_u_r$w_u, fservings_tbls_u_r$w_r)
tbl_b_u_r <- rbind(fservings_tbls_u_r$b_u, fservings_tbls_u_r$b_r)

cbind(tbl_m_u_r, select(tbl_w_u_r, -agerange2), select(tbl_b_u_r, -agerange2)) %>% 
  final_tbl(.disaggregation = u_r, .s_amount = 3, .title = "Mean number of servings of fruit on average per day by type of settlement", .colspan_val = 10)
```

<br>

```{r, eval=.GlobalEnv$.u_r_reg==TRUE}
# 2. Vegetables
tbl_m_u_r <- rbind(vservings_tbls_u_r$m_u, vservings_tbls_u_r$m_r)
tbl_w_u_r <- rbind(vservings_tbls_u_r$w_u, vservings_tbls_u_r$w_r)
tbl_b_u_r <- rbind(vservings_tbls_u_r$b_u, vservings_tbls_u_r$b_r)

cbind(tbl_m_u_r, select(tbl_w_u_r, -agerange2), select(tbl_b_u_r, -agerange2)) %>% 
  final_tbl(.disaggregation = u_r, .s_amount = 3, .title = "Mean number of servings of vegetables on average per day by type of settlement", .colspan_val = 10)
```

<br>

```{r, eval=.GlobalEnv$.u_r_reg==TRUE}
# 3. Fruit and/or vegetables
tbl_m_u_r <- rbind(fvservings_tbls_u_r$m_u, fvservings_tbls_u_r$m_r)
tbl_w_u_r <- rbind(fvservings_tbls_u_r$w_u, fvservings_tbls_u_r$w_r)
tbl_b_u_r <- rbind(fvservings_tbls_u_r$b_u, fvservings_tbls_u_r$b_r)

cbind(tbl_m_u_r, select(tbl_w_u_r, -agerange2), select(tbl_b_u_r, -agerange2)) %>% 
  final_tbl(.disaggregation = u_r, .s_amount = 3, .title = "Mean number of servings of fruit and/or vegetables on average per day by type of settlement", .colspan_val = 10)
```

<br>

```{r, eval=.GlobalEnv$.u_r_reg==TRUE}
# 1. Fruit
fservings_tbls$b_reg %>% unite_ci(.ci_amount = 1) %>% apply_hux(.col_names = dservings_reg_col_names) %>% 
  final_tbl(.disaggregation = reg, 1, "Both sexes", "Mean number of servings of fruit on average per day by region", 4) 
```

<br>

```{r, eval=.GlobalEnv$.u_r_reg==TRUE}
# 2. Veges
vservings_tbls$b_reg %>% unite_ci(.ci_amount = 1) %>% apply_hux(.col_names = dservings_reg_col_names) %>% 
  final_tbl(.disaggregation = reg, 1, "Both sexes", "Mean number of servings of vegetables on average per day by region", 4) 
```

<br>

```{r, eval=.GlobalEnv$.u_r_reg==TRUE}
# 3. Fruit and/or veges
fvservings_tbls$b_reg %>% unite_ci(.ci_amount = 1) %>% apply_hux(.col_names = dservings_reg_col_names) %>% 
  final_tbl(.disaggregation = reg, 1, "Both sexes", "Mean number of servings of fruit and/or vegetables on average per day by region", 4) 
```

<br>

**Analysis information**:

- Questions used: D1, D2, D3, D4
- R script name: Dservings

***

**Fruit and vegetable consumption per day**

Description: Frequency of fruit and/or vegetable consumption.

Instrument questions:

- In a typical week, on how many days do you eat fruit?
- How many servings of fruit do you eat on one of those days?
- In a typical week, on how many days do you eat vegetables?
- How many servings of vegetables do you eat on one of those days?

```{r dfiveormore_d_tbls}

# column names to use with huxtable
dfiveormore_d_col_names <- c("Age Group (years)", "n", 
                             "% no fruit and/or vegetables", "95% CI", 
                             "% 1-2 servings", "95% CI", 
                             "% 3-4 servings ", "95% CI", 
                             "% ≥5 servings", "95% CI")

# column names for region to use with huxtable
dfiveormore_d_reg_col_names <- c("Region", "n", 
                                 "% no fruit and/or vegetables", "95% CI", 
                                 "% 1-2 servings", "95% CI", 
                                 "% 3-4 servings ", "95% CI", 
                                 "% ≥5 servings", "95% CI")

# men, women, both sexes
dfiveormore_d_m_w_b <- join_tbls(dfiveormore_d, m_w_b, 4, dfiveormore_d_col_names)
```
```{r, eval=.GlobalEnv$.u_r_reg==TRUE}
# urban, rural
dfiveormore_d_u_r <- join_tbls(dfiveormore_d, u_r, 4, dfiveormore_d_col_names)
```

<br>

```{r}
dfiveormore_d_m_w_b$m %>% final_tbl(.disaggregation = m_w_b, 1, "Men", "Number of servings of fruit and/or vegetables on average per day", 10)
```

<br>

```{r}
dfiveormore_d_m_w_b$w %>% final_tbl(.disaggregation = m_w_b, 1, "Women", "Number of servings of fruit and/or vegetables on average per day", 10)
```

<br>

```{r}
dfiveormore_d_m_w_b$b %>% final_tbl(.disaggregation = m_w_b, 1, "Both sexes", "Number of servings of fruit and/or vegetables on average per day", 10)
```

<br>

```{r, eval=.GlobalEnv$.u_r_reg==TRUE}
rbind(dfiveormore_d_u_r$m_u, dfiveormore_d_u_r$m_r) %>% 
  final_tbl(.disaggregation = u_r, 1, "Men", "Number of servings of fruit and/or vegetables on average per day by type of settlement", 10)
```

<br>

```{r, eval=.GlobalEnv$.u_r_reg==TRUE}
rbind(dfiveormore_d_u_r$w_u, dfiveormore_d_u_r$w_r) %>% 
  final_tbl(.disaggregation = u_r, 1, "Women", "Number of servings of fruit and/or vegetables on average per day by type of settlement", 10)
```

<br>

```{r, eval=.GlobalEnv$.u_r_reg==TRUE}
rbind(dfiveormore_d_u_r$b_u, dfiveormore_d_u_r$b_r) %>% 
  final_tbl(.disaggregation = u_r, 1, "Both sexes", "Number of servings of fruit and/or vegetables on average per day by type of settlement", 10)
```

<br>

```{r, eval=.GlobalEnv$.u_r_reg==TRUE}
# region
dfiveormore_d$b_reg %>% unite_ci(.ci_amount = 4) %>% apply_hux(.col_names = dfiveormore_d_reg_col_names) %>% 
  final_tbl(.disaggregation = reg, 1, "Both sexes", "Number of servings of fruit and/or vegetables on average per day by region", 10) 
```

<br>

**Analysis information**:

- Questions used: D1, D2, D3, D4
- R script name: Dfiveormore

***

**Fruit and vegetable consumption per day**

Description: Percentage of those eating less than five servings of fruit and/or vegetables on average per day.

Instrument questions:

- In a typical week, on how many days do you eat fruit?
- How many servings of fruit do you eat on one of those days?
- In a typical week, on how many days do you eat vegetables?
- How many servings of vegetables do you eat on one of those days?

```{r dfiveormore_c_tbls}

# column names to use with huxtable
dfiveormore_c_col_names <- c("Age Group (years)", "n", "% < five servings per day", "95% CI")
dfiveormore_c_reg_col_names <- c("Region", "n", "% < five servings per day", "95% CI")

# men, women, both sexes
dfiveormore_c_m_w_b <- join_tbls(dfiveormore_c, m_w_b, 1, dfiveormore_c_col_names)
```
```{r, eval=.GlobalEnv$.u_r_reg==TRUE}
# urban, rural
dfiveormore_c_u_r <- join_tbls(dfiveormore_c, u_r, 1, dfiveormore_c_col_names)
```

<br>

```{r}
cbind(dfiveormore_c_m_w_b$m, select(dfiveormore_c_m_w_b$w, -agerange), select(dfiveormore_c_m_w_b$b, -agerange)) %>% 
  final_tbl(.disaggregation = m_w_b, .s_amount = 3, .title = "Less than five servings of fruit and/or vegetables on average per day", .colspan_val = 10)
```

<br>

```{r, eval=.GlobalEnv$.u_r_reg==TRUE}
tbl_m_u_r <- rbind(dfiveormore_c_u_r$m_u, dfiveormore_c_u_r$m_r)
tbl_w_u_r <- rbind(dfiveormore_c_u_r$w_u, dfiveormore_c_u_r$w_r)
tbl_b_u_r <- rbind(dfiveormore_c_u_r$b_u, dfiveormore_c_u_r$b_r)

cbind(tbl_m_u_r, select(tbl_w_u_r, -agerange2), select(tbl_b_u_r, -agerange2)) %>% 
  final_tbl(.disaggregation = u_r, .s_amount = 3, .title = "Less than five servings of fruit and/or vegetables on average per day by type of settlement", .colspan_val = 10)
```

<br>

```{r, eval=.GlobalEnv$.u_r_reg==TRUE}
dfiveormore_c$b_reg %>% unite_ci(.ci_amount = 1) %>% apply_hux(.col_names = dfiveormore_c_reg_col_names) %>% 
  final_tbl(.disaggregation = reg, 1, "Both sexes", "Less than five servings of fruit and/or vegetables on average per day by region", 4) 
```

<br>

**Analysis information**:

- Questions used: D1, D2, D3, D4
- R script name: Dfiveormore

***

**Adding salt at meal**

Description: Percentage of all respondents who always or often add salt or salty sauce to their food before eating or as they are eating.

Instrument questions:

- How often do you add salt or a salty sauce such as soya sauce to your food right before you eat it or as you are eating it?

```{r deating_c_tbls}

# column names to use with huxtable
deating_c_col_names <- c("Age Group (years)", "n", "%", "95% CI")
deating_c_reg_col_names <- c("Region", "n", "%", "95% CI")

# men, women, both sexes
deating_c_m_w_b <- join_tbls(deating_c, m_w_b, 1, deating_c_col_names)
```
```{r, eval=.GlobalEnv$.u_r_reg==TRUE}
# urban, rural
deating_c_u_r <- join_tbls(deating_c, u_r, 1, deating_c_col_names)
```

<br>

```{r}
cbind(deating_c_m_w_b$m, select(deating_c_m_w_b$w, -agerange), select(deating_c_m_w_b$b, -agerange)) %>% 
  final_tbl(.disaggregation = m_w_b, .s_amount = 3, .title = "Add salt always or often before eating or when eating", .colspan_val = 10)
```

<br>

```{r, eval=.GlobalEnv$.u_r_reg==TRUE}
tbl_m_u_r <- rbind(deating_c_u_r$m_u, deating_c_u_r$m_r)
tbl_w_u_r <- rbind(deating_c_u_r$w_u, deating_c_u_r$w_r)
tbl_b_u_r <- rbind(deating_c_u_r$b_u, deating_c_u_r$b_r)

cbind(tbl_m_u_r, select(tbl_w_u_r, -agerange2), select(tbl_b_u_r, -agerange2)) %>% 
  final_tbl(.disaggregation = u_r, .s_amount = 3, .title = "Add salt always or often before eating or when eating by type of settlement", .colspan_val = 10)
```

<br>

```{r, eval=.GlobalEnv$.u_r_reg==TRUE}
deating_c$b_reg %>% unite_ci(.ci_amount = 1) %>% apply_hux(.col_names = deating_c_reg_col_names) %>% 
  final_tbl(.disaggregation = reg, 1, "Both sexes", "Add salt always or often before eating or when eating by region", 4) 
```

<br>

**Analysis information**:

- Questions used: D5
- R script name: Deating

***

**Adding salt when cooking**

Description: Percentage of all respondents who always or often add salt to their food when cooking or preparing foods at home.

Instrument questions:

- How often is salt, salty seasoning or a salty sauce added in cooking or preparing foods in your household?

```{r dcooking_c_tbls}

# column names to use with huxtable
dcooking_c_col_names <- c("Age Group (years)", "n", "%", "95% CI")
dcooking_c_reg_col_names <- c("Region", "n", "%", "95% CI")

# men, women, both sexes
dcooking_c_m_w_b <- join_tbls(dcooking_c, m_w_b, 1, dcooking_c_col_names)
```
```{r, eval=.GlobalEnv$.u_r_reg==TRUE}
# urban, rural
dcooking_c_u_r <- join_tbls(dcooking_c, u_r, 1, dcooking_c_col_names)
```

<br>

```{r}
cbind(dcooking_c_m_w_b$m, select(dcooking_c_m_w_b$w, -agerange), select(dcooking_c_m_w_b$b, -agerange)) %>% 
  final_tbl(.disaggregation = m_w_b, .s_amount = 3, .title = "Add salt always or often when cooking or preparing food at home", .colspan_val = 10)
```

<br>

```{r, eval=.GlobalEnv$.u_r_reg==TRUE}
tbl_m_u_r <- rbind(dcooking_c_u_r$m_u, dcooking_c_u_r$m_r)
tbl_w_u_r <- rbind(dcooking_c_u_r$w_u, dcooking_c_u_r$w_r)
tbl_b_u_r <- rbind(dcooking_c_u_r$b_u, dcooking_c_u_r$b_r)

cbind(tbl_m_u_r, select(tbl_w_u_r, -agerange2), select(tbl_b_u_r, -agerange2)) %>% 
  final_tbl(.disaggregation = u_r, .s_amount = 3, .title = "Add salt always or often when cooking or preparing food at home by type of settlement", .colspan_val = 10)
```

<br>

```{r, eval=.GlobalEnv$.u_r_reg==TRUE}
dcooking_c$b_reg %>% unite_ci(.ci_amount = 1) %>% apply_hux(.col_names = dcooking_c_reg_col_names) %>% 
  final_tbl(.disaggregation = reg, 1, "Both sexes", "Add salt always or often when cooking or preparing food at home by region", 4) 
```

<br>

**Analysis information**:

- Questions used: D6
- R script name: Dcooking

***

**Salty processed food consumption**

Description: Percentage of all respondents who always or often eat processed foods high in salt.

Instrument questions:

- How often do you eat processed food high in salt?

```{r dprocessed_c_tbls}

# column names to use with huxtable
dprocessed_c_col_names <- c("Age Group (years)", "n", "%", "95% CI")
dprocessed_c_reg_col_names <- c("Region", "n", "%", "95% CI")

# men, women, both sexes
dprocessed_c_m_w_b <- join_tbls(dprocessed_c, m_w_b, 1, dprocessed_c_col_names)
```
```{r, eval=.GlobalEnv$.u_r_reg==TRUE}
# urban, rural
dprocessed_c_u_r <- join_tbls(dprocessed_c, u_r, 1, dprocessed_c_col_names)
```

<br>

```{r}
cbind(dprocessed_c_m_w_b$m, select(dprocessed_c_m_w_b$w, -agerange), select(dprocessed_c_m_w_b$b, -agerange)) %>% 
  final_tbl(.disaggregation = m_w_b, .s_amount = 3, .title = "Always or often consume processed food high in salt", .colspan_val = 10)
```

<br>

```{r, eval=.GlobalEnv$.u_r_reg==TRUE}
tbl_m_u_r <- rbind(dprocessed_c_u_r$m_u, dprocessed_c_u_r$m_r)
tbl_w_u_r <- rbind(dprocessed_c_u_r$w_u, dprocessed_c_u_r$w_r)
tbl_b_u_r <- rbind(dprocessed_c_u_r$b_u, dprocessed_c_u_r$b_r)

cbind(tbl_m_u_r, select(tbl_w_u_r, -agerange2), select(tbl_b_u_r, -agerange2)) %>% 
  final_tbl(.disaggregation = u_r, .s_amount = 3, .title = "Always or often consume processed food high in salt by type of settlement", .colspan_val = 10)
```

<br>

```{r, eval=.GlobalEnv$.u_r_reg==TRUE}
dprocessed_c$b_reg %>% unite_ci(.ci_amount = 1) %>% apply_hux(.col_names = dprocessed_c_reg_col_names) %>% 
  final_tbl(.disaggregation = reg, 1, "Both sexes", "Always or often consume processed food high in salt by region", 4) 
```

<br>

**Analysis information**:

- Questions used: D7
- R script name: Dprocessed

***


**Salt consumption**

Description: Percentage of all respondents who think they consume far too much or too much salt.

Instrument questions:

- How much salt or salty sauce do you think you consume?

```{r dsaltquantity_tbls}

# 1. Think they consume far too much or too much salt
# column names to use with huxtable
dsaltquantity_c_col_names <- c("Age Group (years)", "n", "%", "95% CI")
dsaltquantity_c_reg_col_names <- c("Region", "n", "%", "95% CI")

# men, women, both sexes
dsaltquantity_c_m_w_b <- join_tbls(dsaltquantity_c, m_w_b, 1, dsaltquantity_c_col_names)

################################################################################

# 2. Self-reported quantity of salt consumed
# column names to use with huxtable
dsaltquantity_d_col_names <- 
  c("Age Group (years)", "n", "% Far too much", "95% CI", 
    "% Too much", "95% CI", "% Just the right amount", "95% CI", 
    "% Too little", "95% CI", "% Far too little", "95% CI")

# column names for region to use with huxtable
dsaltquantity_d_reg_col_names <- 
  c("Region", "n", "% Far too much", "95% CI", "% Too much", 
    "95% CI", "% Just the right amount", "95% CI", 
    "% Too little", "95% CI", "% Far too little", "95% CI")

# men, women, both sexes
dsaltquantity_d_m_w_b <- join_tbls(dsaltquantity_d, m_w_b, 5, dsaltquantity_d_col_names)
```
```{r, eval=.GlobalEnv$.u_r_reg==TRUE}
# urban, rural
# 1. Think they consume far too much or too much salt
dsaltquantity_c_u_r <- join_tbls(dsaltquantity_c, u_r, 1, dsaltquantity_c_col_names)
# 2. Self-reported quantity of salt consumed
dsaltquantity_d_u_r <- join_tbls(dsaltquantity_d, u_r, 5, dsaltquantity_d_col_names)
```

<br>

```{r}
# 1. Think they consume far too much or too much salt
cbind(dsaltquantity_c_m_w_b$m, select(dsaltquantity_c_m_w_b$w, -agerange), select(dsaltquantity_c_m_w_b$b, -agerange)) %>% 
  final_tbl(.disaggregation = m_w_b, .s_amount = 3, .title = "Think they consume far too much or too much salt", .colspan_val = 10)
```

<br>

```{r}
# 2. Self-reported quantity of salt consumed
dsaltquantity_d_m_w_b$m %>% final_tbl(.disaggregation = m_w_b, 1, "Men", "Self-reported quantity of salt consumed", 12)
```

<br>

```{r}
# 2. Self-reported quantity of salt consumed
dsaltquantity_d_m_w_b$w %>% final_tbl(.disaggregation = m_w_b, 1, "Women", "Self-reported quantity of salt consumed", 12)
```

<br>

```{r}
# 2. Self-reported quantity of salt consumed
dsaltquantity_d_m_w_b$b %>% final_tbl(.disaggregation = m_w_b, 1, "Both sexes", "Self-reported quantity of salt consumed", 12)
```

<br>

```{r, eval=.GlobalEnv$.u_r_reg==TRUE}
# 1. Think they consume far too much or too much salt
tbl_m_u_r <- rbind(dsaltquantity_c_u_r$m_u, dsaltquantity_c_u_r$m_r)
tbl_w_u_r <- rbind(dsaltquantity_c_u_r$w_u, dsaltquantity_c_u_r$w_r)
tbl_b_u_r <- rbind(dsaltquantity_c_u_r$b_u, dsaltquantity_c_u_r$b_r)

cbind(tbl_m_u_r, select(tbl_w_u_r, -agerange2), select(tbl_b_u_r, -agerange2)) %>% 
  final_tbl(.disaggregation = u_r, .s_amount = 3, .title = "Think they consume far too much or too much salt by type of settlement", .colspan_val = 10)
```

<br>

```{r, eval=.GlobalEnv$.u_r_reg==TRUE}
# 2. Self-reported quantity of salt consumed
rbind(dsaltquantity_d_u_r$m_u, dsaltquantity_d_u_r$m_r) %>% 
  final_tbl(.disaggregation = u_r, 1, "Men", "Self-reported quantity of salt consumed by type of settlement", 12)
```

<br>

```{r, eval=.GlobalEnv$.u_r_reg==TRUE}
# 2. Self-reported quantity of salt consumed
rbind(dsaltquantity_d_u_r$w_u, dsaltquantity_d_u_r$w_r) %>% 
  final_tbl(.disaggregation = u_r, 1, "Women", "Self-reported quantity of salt consumed by type of settlement", 12)
```

<br>

```{r, eval=.GlobalEnv$.u_r_reg==TRUE}
# 2. Self-reported quantity of salt consumed
rbind(dsaltquantity_d_u_r$b_u, dsaltquantity_d_u_r$b_r) %>% 
  final_tbl(.disaggregation = u_r, 1, "Both sexes", "Self-reported quantity of salt consumed by type of settlement", 12)
```

<br>

```{r, eval=.GlobalEnv$.u_r_reg==TRUE}
# 1. Think they consume far too much or too much salt
dsaltquantity_c$b_reg %>% unite_ci(.ci_amount = 1) %>% apply_hux(.col_names = dsaltquantity_c_reg_col_names) %>% 
  final_tbl(.disaggregation = reg, 1, "Both sexes", "Think they consume far too much or too much salt by region", 4) 
```

<br>

```{r, eval=.GlobalEnv$.u_r_reg==TRUE}
# 2. Self-reported quantity of salt consumed
dsaltquantity_d$b_reg %>% unite_ci(.ci_amount = 5) %>% apply_hux(.col_names = dsaltquantity_d_reg_col_names) %>% 
  final_tbl(.disaggregation = reg, 1, "Both sexes", "Self-reported quantity of salt consumed by region", 12) 
```

<br>

**Analysis information**:

- Questions used: D8
- R script name: Dsaltquantity

***

**Lowering salt**

Description: Percentage of respondents who think lowering salt in diet is very, somewhat or not at all important.

Instrument questions:

- How important to you is lowering the salt in your diet?

```{r dlower_c_tbls}

# column names to use with huxtable
dlower_c_col_names <- 
  c("Age Group (years)", "n", "% Very important", "95% CI",
    "% Somewhat important", "95% CI", "% Not at all important", "95% CI")

dlower_c_reg_col_names <- 
  c("Region", "n", "% Very important", "95% CI",
    "% Somewhat important", "95% CI", "% Not at all important", "95% CI")

# men, women, both sexes
dlower_c_m_w_b <- join_tbls(dlower_c, m_w_b, 3, dlower_c_col_names)
```
```{r, eval=.GlobalEnv$.u_r_reg==TRUE}
# urban, rural
dlower_c_u_r <- join_tbls(dlower_c, u_r, 3, dlower_c_col_names)
```

<br>

```{r}
dlower_c_m_w_b$m %>% final_tbl(.disaggregation = m_w_b, 1, "Men", "Importance of lowering salt in diet", 8) 
```

<br>

```{r}
dlower_c_m_w_b$w %>% final_tbl(.disaggregation = m_w_b, 1, "Women", "Importance of lowering salt in diet", 8)
```

<br>

```{r}
dlower_c_m_w_b$b %>% final_tbl(.disaggregation = m_w_b, 1, "Both sexes", "Importance of lowering salt in diet", 8)
```

<br>

```{r, eval=.GlobalEnv$.u_r_reg==TRUE}
rbind(dlower_c_u_r$m_u, dlower_c_u_r$m_r) %>% 
  final_tbl(.disaggregation = u_r, 1, "Men", "Importance of lowering salt in diet by type of settlement", 8) 
```

<br>

```{r, eval=.GlobalEnv$.u_r_reg==TRUE}
rbind(dlower_c_u_r$w_u, dlower_c_u_r$w_r) %>% 
  final_tbl(.disaggregation = u_r, 1, "Women", "Importance of lowering salt in diet by type of settlement", 8)
```

<br>

```{r, eval=.GlobalEnv$.u_r_reg==TRUE}
rbind(dlower_c_u_r$b_u, dlower_c_u_r$b_r) %>% 
  final_tbl(.disaggregation = u_r, 1, "Both sexes", "Importance of lowering salt in diet by type of settlement", 8)
```

<br>

```{r, eval=.GlobalEnv$.u_r_reg==TRUE}
# region
dlower_c$b_reg %>% unite_ci(.ci_amount = 3) %>% apply_hux(.col_names = dlower_c_reg_col_names) %>% 
  final_tbl(.disaggregation = reg, 1, "Both sexes", "Importance of lowering salt in diet by region", 8)
```

<br>

**Analysis information**:

- Questions used: D9
- R script name: Dlower

***

**Salt knowledge**

Description: Percentage of respondents who think consuming too much salt could cause a serious health problem.

Instrument questions:

- Do you think that too much salt or salty sauce in your diet could cause a health problem?

```{r dhealth_c_tbls}

# column names to use with huxtable
dhealth_c_col_names <- c("Age Group (years)", "n", "%", "95% CI")
dhealth_c_reg_col_names <- c("Region", "n", "%", "95% CI")

# men, women, both sexes
dhealth_c_m_w_b <- join_tbls(dhealth_c, m_w_b, 1, dhealth_c_col_names)
```
```{r, eval=.GlobalEnv$.u_r_reg==TRUE}
# urban, rural
dhealth_c_u_r <- join_tbls(dhealth_c, u_r, 1, dhealth_c_col_names)
```

<br>

```{r}
cbind(dhealth_c_m_w_b$m, select(dhealth_c_m_w_b$w, -agerange), select(dhealth_c_m_w_b$b, -agerange)) %>% 
  final_tbl(.disaggregation = m_w_b, .s_amount = 3, .title = "Think consuming too much salt could cause serious health problem", .colspan_val = 10)
```

<br>

```{r, eval=.GlobalEnv$.u_r_reg==TRUE}
tbl_m_u_r <- rbind(dhealth_c_u_r$m_u, dhealth_c_u_r$m_r)
tbl_w_u_r <- rbind(dhealth_c_u_r$w_u, dhealth_c_u_r$w_r)
tbl_b_u_r <- rbind(dhealth_c_u_r$b_u, dhealth_c_u_r$b_r)

cbind(tbl_m_u_r, select(tbl_w_u_r, -agerange2), select(tbl_b_u_r, -agerange2)) %>% 
  final_tbl(.disaggregation = u_r, .s_amount = 3, .title = "Think consuming too much salt could cause serious health problem by type of settlement", .colspan_val = 10)
```

<br>

```{r, eval=.GlobalEnv$.u_r_reg==TRUE}
dhealth_c$b_reg %>% unite_ci(.ci_amount = 1) %>% apply_hux(.col_names = dhealth_c_reg_col_names) %>% 
  final_tbl(.disaggregation = reg, 1, "Both sexes", "Think consuming too much salt could cause serious health problem by region", 4) 
```

<br>

**Analysis information**:

- Questions used: D10
- R script name: Dhealth

***

**Controlling salt intake**

Description: Percentage of respondents who take specific action on a regular basis to control salt intake.

Instrument questions:

- Do you do any of the following on a regular basis to control your salt intake?

```{r dcontrol_tbls}
# column names to use with huxtable
dcontrol_col_names <- c("Age Group (years)", "n", "%", "95% CI")
dcontrol_reg_col_names <- c("Region", "n", "%", "95% CI")

# men, women, both sexes
# 1. Limit consumption of processed foods
dcontrol_a_m_w_b <- join_tbls(dcontrol_a, m_w_b, 1, dcontrol_col_names)
# 2. Look at the salt or sodium content on food labels
dcontrol_b_m_w_b <- join_tbls(dcontrol_b, m_w_b, 1, dcontrol_col_names)
# 3. Buy low salt/sodium alternatives
dcontrol_c_m_w_b <- join_tbls(dcontrol_c, m_w_b, 1, dcontrol_col_names)
# 4. Use spices other than salt when cooking
dcontrol_d_m_w_b <- join_tbls(dcontrol_d, m_w_b, 1, dcontrol_col_names)
# 5. Avoid eating foods prepared outside of a home
dcontrol_e_m_w_b <- join_tbls(dcontrol_e, m_w_b, 1, dcontrol_col_names)
# 6. Do other things specifically to control your salt intake
dcontrol_f_m_w_b <- join_tbls(dcontrol_f, m_w_b, 1, dcontrol_col_names)

```
```{r, eval=.GlobalEnv$.u_r_reg==TRUE}
# urban, rural
# 1. Limit consumption of processed foods
dcontrol_a_u_r <- join_tbls(dcontrol_a, u_r, 1, dcontrol_col_names)
# 2. Look at the salt or sodium content on food labels
dcontrol_b_u_r <- join_tbls(dcontrol_b, u_r, 1, dcontrol_col_names)
# 3. Buy low salt/sodium alternatives
dcontrol_c_u_r <- join_tbls(dcontrol_c, u_r, 1, dcontrol_col_names)
# 4. Use spices other than salt when cooking
dcontrol_d_u_r <- join_tbls(dcontrol_d, u_r, 1, dcontrol_col_names)
# 5. Avoid eating foods prepared outside of a home
dcontrol_e_u_r <- join_tbls(dcontrol_e, u_r, 1, dcontrol_col_names)
# 6. Do other things specifically to control your salt intake
dcontrol_f_u_r <- join_tbls(dcontrol_f, u_r, 1, dcontrol_col_names)
```

<br>

```{r}
# 1
cbind(dcontrol_a_m_w_b$m, select(dcontrol_a_m_w_b$w, -agerange), select(dcontrol_a_m_w_b$b, -agerange)) %>% 
  final_tbl(.disaggregation = m_w_b, .s_amount = 3, .title = "Limit consumption of processed foods", .colspan_val = 10)
```

```{r}
# 2
cbind(dcontrol_b_m_w_b$m, select(dcontrol_b_m_w_b$w, -agerange), select(dcontrol_b_m_w_b$b, -agerange)) %>% 
  final_tbl(.disaggregation = m_w_b, .s_amount = 3, .title = "Look at the salt or sodium content on food labels", .colspan_val = 10)
```

```{r}
# 3
cbind(dcontrol_c_m_w_b$m, select(dcontrol_c_m_w_b$w, -agerange), select(dcontrol_c_m_w_b$b, -agerange)) %>% 
  final_tbl(.disaggregation = m_w_b, .s_amount = 3, .title = "Buy low salt/sodium alternatives", .colspan_val = 10)
```

```{r}
# 4
cbind(dcontrol_d_m_w_b$m, select(dcontrol_d_m_w_b$w, -agerange), select(dcontrol_d_m_w_b$b, -agerange)) %>% 
  final_tbl(.disaggregation = m_w_b, .s_amount = 3, .title = "Use spices other than salt when cooking", .colspan_val = 10)
```

```{r}
# 5
cbind(dcontrol_e_m_w_b$m, select(dcontrol_e_m_w_b$w, -agerange), select(dcontrol_e_m_w_b$b, -agerange)) %>% 
  final_tbl(.disaggregation = m_w_b, .s_amount = 3, .title = "Avoid eating foods prepared outside of a home", .colspan_val = 10)
```

```{r}
# 6
cbind(dcontrol_f_m_w_b$m, select(dcontrol_f_m_w_b$w, -agerange), select(dcontrol_f_m_w_b$b, -agerange)) %>% 
  final_tbl(.disaggregation = m_w_b, .s_amount = 3, .title = "Do other things specifically to control your salt intake", .colspan_val = 10)
```

<br>

```{r, eval=.GlobalEnv$.u_r_reg==TRUE}
# 1
tbl_m_u_r <- rbind(dcontrol_a_u_r$m_u, dcontrol_a_u_r$m_r)
tbl_w_u_r <- rbind(dcontrol_a_u_r$w_u, dcontrol_a_u_r$w_r)
tbl_b_u_r <- rbind(dcontrol_a_u_r$b_u, dcontrol_a_u_r$b_r)

cbind(tbl_m_u_r, select(tbl_w_u_r, -agerange2), select(tbl_b_u_r, -agerange2)) %>% 
  final_tbl(.disaggregation = u_r, .s_amount = 3, .title = "Limit consumption of processed foods by type of settlement", .colspan_val = 10)
```

<br>

```{r, eval=.GlobalEnv$.u_r_reg==TRUE}
# 2
tbl_m_u_r <- rbind(dcontrol_b_u_r$m_u, dcontrol_b_u_r$m_r)
tbl_w_u_r <- rbind(dcontrol_b_u_r$w_u, dcontrol_b_u_r$w_r)
tbl_b_u_r <- rbind(dcontrol_b_u_r$b_u, dcontrol_b_u_r$b_r)

cbind(tbl_m_u_r, select(tbl_w_u_r, -agerange2), select(tbl_b_u_r, -agerange2)) %>% 
  final_tbl(.disaggregation = u_r, .s_amount = 3, .title = "Look at the salt or sodium content on food labels by type of settlement", .colspan_val = 10)
```

<br>

```{r, eval=.GlobalEnv$.u_r_reg==TRUE}
# 3
tbl_m_u_r <- rbind(dcontrol_c_u_r$m_u, dcontrol_c_u_r$m_r)
tbl_w_u_r <- rbind(dcontrol_c_u_r$w_u, dcontrol_c_u_r$w_r)
tbl_b_u_r <- rbind(dcontrol_c_u_r$b_u, dcontrol_c_u_r$b_r)

cbind(tbl_m_u_r, select(tbl_w_u_r, -agerange2), select(tbl_b_u_r, -agerange2)) %>% 
  final_tbl(.disaggregation = u_r, .s_amount = 3, .title = "Buy low salt/sodium alternatives by type of settlement", .colspan_val = 10)
```

<br>

```{r, eval=.GlobalEnv$.u_r_reg==TRUE}
# 4
tbl_m_u_r <- rbind(dcontrol_d_u_r$m_u, dcontrol_d_u_r$m_r)
tbl_w_u_r <- rbind(dcontrol_d_u_r$w_u, dcontrol_d_u_r$w_r)
tbl_b_u_r <- rbind(dcontrol_d_u_r$b_u, dcontrol_d_u_r$b_r)

cbind(tbl_m_u_r, select(tbl_w_u_r, -agerange2), select(tbl_b_u_r, -agerange2)) %>% 
  final_tbl(.disaggregation = u_r, .s_amount = 3, .title = "Use spices other than salt when cooking by type of settlement", .colspan_val = 10)
```

<br>

```{r, eval=.GlobalEnv$.u_r_reg==TRUE}
# 5
tbl_m_u_r <- rbind(dcontrol_e_u_r$m_u, dcontrol_e_u_r$m_r)
tbl_w_u_r <- rbind(dcontrol_e_u_r$w_u, dcontrol_e_u_r$w_r)
tbl_b_u_r <- rbind(dcontrol_e_u_r$b_u, dcontrol_e_u_r$b_r)

cbind(tbl_m_u_r, select(tbl_w_u_r, -agerange2), select(tbl_b_u_r, -agerange2)) %>% 
  final_tbl(.disaggregation = u_r, .s_amount = 3, .title = "Avoid eating foods prepared outside of a home by type of settlement", .colspan_val = 10)
```

<br>

```{r, eval=.GlobalEnv$.u_r_reg==TRUE}
# 6
tbl_m_u_r <- rbind(dcontrol_f_u_r$m_u, dcontrol_f_u_r$m_r)
tbl_w_u_r <- rbind(dcontrol_f_u_r$w_u, dcontrol_f_u_r$w_r)
tbl_b_u_r <- rbind(dcontrol_f_u_r$b_u, dcontrol_f_u_r$b_r)

cbind(tbl_m_u_r, select(tbl_w_u_r, -agerange2), select(tbl_b_u_r, -agerange2)) %>% 
  final_tbl(.disaggregation = u_r, .s_amount = 3, .title = "Do other things specifically to control your salt intake by type of settlement", .colspan_val = 10)
```

<br>

```{r, eval=.GlobalEnv$.u_r_reg==TRUE}
# 1
dcontrol_a$b_reg %>% unite_ci(.ci_amount = 1) %>% apply_hux(.col_names = dcontrol_reg_col_names) %>% 
  final_tbl(.disaggregation = reg, 1, "Both sexes", "Limit consumption of processed foods by region", 4) 
```

<br>

```{r, eval=.GlobalEnv$.u_r_reg==TRUE}
# 2
dcontrol_b$b_reg %>% unite_ci(.ci_amount = 1) %>% apply_hux(.col_names = dcontrol_reg_col_names) %>% 
  final_tbl(.disaggregation = reg, 1, "Both sexes", "Look at the salt or sodium content on food labels by region", 4) 
```

<br>

```{r, eval=.GlobalEnv$.u_r_reg==TRUE}
# 3
dcontrol_c$b_reg %>% unite_ci(.ci_amount = 1) %>% apply_hux(.col_names = dcontrol_reg_col_names) %>% 
  final_tbl(.disaggregation = reg, 1, "Both sexes", "Buy low salt/sodium alternatives by region", 4) 
```

<br>

```{r, eval=.GlobalEnv$.u_r_reg==TRUE}
# 4
dcontrol_d$b_reg %>% unite_ci(.ci_amount = 1) %>% apply_hux(.col_names = dcontrol_reg_col_names) %>% 
  final_tbl(.disaggregation = reg, 1, "Both sexes", "Use spices other than salt when cooking by region", 4) 
```

<br>

```{r, eval=.GlobalEnv$.u_r_reg==TRUE}
# 5
dcontrol_e$b_reg %>% unite_ci(.ci_amount = 1) %>% apply_hux(.col_names = dcontrol_reg_col_names) %>% 
  final_tbl(.disaggregation = reg, 1, "Both sexes", "Avoid eating foods prepared outside of a home by region", 4) 
```

<br>

```{r, eval=.GlobalEnv$.u_r_reg==TRUE}
# 6
dcontrol_f$b_reg %>% unite_ci(.ci_amount = 1) %>% apply_hux(.col_names = dcontrol_reg_col_names) %>% 
  final_tbl(.disaggregation = reg, 1, "Both sexes", "Do other things specifically to control your salt intake by region", 4) 
```

<br>

**Analysis information**:

- Questions used: D11a-f
- R script name: Dcontrol

***


**Drinking sugared soft drinks**

Description: How often people drink sugared beverages, excluding light, diet and non-sugar beverages.

Instrument questions:

- How often do you drink sugared soft drinks (for example, Coca Cola, Pepsi, Fanta, Sprite, Mirinda, Kvas, Baikal, Buratino, Tarkhun etc.), bottled ice tea (for example, Nestea, Lipton Ice Tea, etc.) and sugar sweetened compote, sweet mors? Exclude light, diet and non-sugar drinks.

```{r dx1_tbls, echo=FALSE}
# column names to use with huxtable
dx1_col_names <- 
  c("Age Group (years)", "n", "% Once or more a day", 
    "95% CI", "% 4 to 6 times a week", "95% CI", 
    "% 1 to 3 times a week", "95% CI", 
    "% Less than once a week", "95% CI", "% Never", "95% CI")

# column names for region to use with huxtable
dx1_reg_col_names <- 
  c("Region", "n", "% Once or more a day", "95% CI", 
    "% 4 to 6 times a week", "95% CI", 
    "% 1 to 3 times a week", "95% CI", 
    "% Less than once a week", "95% CI", "% Never", "95% CI")

# men, women, both sexes
dx1_c_m_w_b <- join_tbls(dx1_c, m_w_b, 5, dx1_col_names)
```
```{r, eval=.GlobalEnv$.u_r_reg==TRUE}
# urban, rural
dx1_c_u_r <- join_tbls(dx1_c, u_r, 5, dx1_col_names)
```

<br>

```{r}
dx1_c_m_w_b$m %>% final_tbl(.disaggregation = m_w_b, .s_amount = 1, .s_val = "Men", .title = "Drinking sugared soft drinks", .colspan_val = 12)
```

<br>

```{r}
dx1_c_m_w_b$w %>% final_tbl(.disaggregation = m_w_b, .s_amount = 1, .s_val = "Women", .title = "Drinking sugared soft drinks", .colspan_val = 12)
```

<br>

```{r}
dx1_c_m_w_b$b %>% final_tbl(.disaggregation = m_w_b, .s_amount = 1, .s_val = "Both sexes", .title = "Drinking sugared soft drinks", .colspan_val = 12)
```

<br>

```{r, eval=.GlobalEnv$.u_r_reg==TRUE}
rbind(dx1_c_u_r$m_u, dx1_c_u_r$m_r) %>% 
  final_tbl(.disaggregation = u_r, .s_amount = 1, .s_val = "Men", .title = "Drinking sugared soft drinks by type of settlement", .colspan_val = 12)
```

<br>

```{r, eval=.GlobalEnv$.u_r_reg==TRUE}
rbind(dx1_c_u_r$w_u, dx1_c_u_r$w_r) %>% 
  final_tbl(.disaggregation = u_r, .s_amount = 1, .s_val = "Women", .title = "Drinking sugared soft drinks by type of settlement", .colspan_val = 12)
```

<br>

```{r, eval=.GlobalEnv$.u_r_reg==TRUE}
rbind(dx1_c_u_r$b_u, dx1_c_u_r$b_r) %>% 
  final_tbl(.disaggregation = u_r, .s_amount = 1, .s_val = "Both sexes", .title = "Drinking sugared soft drinks by type of settlement", .colspan_val = 12)
```

<br>

```{r, eval=.GlobalEnv$.u_r_reg==TRUE}
# region
dx1_c$b_reg %>% unite_ci(.ci_amount = 5) %>% apply_hux(.col_names = dx1_reg_col_names) %>% 
  final_tbl(.disaggregation = reg, .s_amount = 1, .s_val = "Both sexes", .title = "Drinking sugared soft drinks by region", .colspan_val = 12)
```

<br>

**Analysis information**:

- Questions used: DX1
- R script name: DX1

***



<br>
<br>
